### 2024-03-28 paper/paper.qmd
add raw data and remove replication.R

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

#download the packages if necessary, then load the packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2)

library(janitor)
library(tidyverse)
library(knitr)
library(dplyr)
library(kableExtra)
library(here)
library(ggplot2)
```

# Introduction {#sec-intro}

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@GSS]. From the dataset, this paper focuses on the "number of hours worked last week" variable, from the years 1992 to 2022. This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.

## Source Data

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results {#sec-results}

Our results are summarized in @tbl-modelresults.

# Discussion {#sec-discussion}

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

\newpage

# References

### 2024-03-28 scripts/00-simulate_data.R
updated simulated data and test cases

@@ -1,19 +1,32 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates the raw dataset for code testing
+# Author: Mingjia Chen
+# Date: 28 March 2023
+# Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: R
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+simulated_data <-
+  tibble(
+    mental_health =runif(n = 1000,min = 0,max = 7) |> floor(),
+    physical_health = runif(n = 1000,min = 0,max = 7) |> floor(),
+)
 
+# expected that mental_health is only between 0 to 6
+# expected that  physical_health is only between 0 to 6
 
+#### Add tests for simulated data ####
 
+# expected that mental_health is only between 0 to 6
+any(unique(simulated_data$mental_health)) == c(0:6)
+min(simulated_data$mental_health) == 0
+max(simulated_data$mental_health) == 6
+# expected that  physical_health is only between 0 to 6
+any(unique(simulated_data$physical_health)) == c(0:6)
+min(simulated_data$physical_health) == 0
+max(simulated_data$physical_health) == 6

### 2024-03-28 scripts/00-simulate_data.R
Update simulate_data.R, data_cleaning.R, and raw dataset for the study

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Simulates the raw dataset for code testing
 # Author: Mingjia Chen
-# Date: 28 March 2023
+# Date: 28 March 2024
 # Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: R

### 2024-03-28 scripts/02-data_cleaning.R

@@ -1,44 +1,64 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data recorded by U.S.General Social Survey (GSS)
+# Author: Mingjia Chen
+# Date: 28 March 2024
+# Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Have to manually download the data from the raw data folder.
+# Any other information needed? -
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
+
+#### Load data ####
+# This part of the code is from GSS Open Explore
+
+# When downloading the dataset from the website, the R script can be chosen to
+# be downloaded as well.
+
+#After running this part of the code, the data will be available for modifying
+# and analyzing.
+
+library(foreign)
+read.dct <- function(dct, labels.included = "yes") {
+  temp <- readLines(dct)
+  temp <- temp[grepl("_column", temp)]
+  switch(labels.included,
+         yes = {
+           pattern <- "_column\\(([0-9]+)\\)\\s+([a-z0-9]+)\\s+(.*)\\s+%([0-9]+)[a-z]\\s+(.*)"
+           classes <- c("numeric", "character", "character", "numeric", "character")
+           N <- 5
+           NAMES <- c("StartPos", "Str", "ColName", "ColWidth", "ColLabel")
+         },
+         no = {
+           pattern <- "_column\\(([0-9]+)\\)\\s+([a-z0-9]+)\\s+(.*)\\s+%([0-9]+).*"
+           classes <- c("numeric", "character", "character", "numeric")
+           N <- 4
+           NAMES <- c("StartPos", "Str", "ColName", "ColWidth")
+         })
+  temp_metadata <- setNames(lapply(1:N, function(x) {
+    out <- gsub(pattern, paste("\\", x, sep = ""), temp)
+    out <- gsub("^\\s+|\\s+$", "", out)
+    out <- gsub('\"', "", out, fixed = TRUE)
+    class(out) <- classes[x] ; out }), NAMES)
[…]

### 2024-03-28 paper/paper.qmd
update paper table

@@
 This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.
+
+For the analysis, we retrieved the following data as described in @tbl-use-var.
+
+| Variable | New Name   | Description                     | Example |
+|----------|------------|---------------------------------|---------|
+| sex      | sex        | Respondent's gender             |2(FEMALE)|
+| HEALTH   | health     | The year of the survey recorded | 2007    |
+| SATHEALT | AGE        | The age of the respondents      | 23      |
+| PHYSHLTH | Phys_Health| Respondents' physical health    | MALE    |
+
+: Source data retrieved from GSS {#tbl-use-var}
 

### 2024-03-28 paper/paper.qmd
update sketches and paper (table)

--- 2024-03-28 paper/paper.qmd
@@
 This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.
+
+For the analysis, we retrieved the following data as described in @tbl-use-var.
+
+| Variable | New Name   | Description                     | Example |
+|----------|------------|---------------------------------|---------|
+| sex      | sex        | Respondent's gender             | Female  |
+| age      | age        | Respondent's age                | 25      |
+| HEALTH   | health     | Respondents' health condition   | Good    |
+| SATHEALT | AGE        | The age of the respondents      | 23      |
+| PHYSHLTH | Phys_Health| Respondents' physical health    | MALE    |
+
+: Source data retrieved from GSS {#tbl-use-var}
 

### 2024-03-28 paper/paper.qmd
removed unused literature and update paper data table

--- 2024-03-28 paper/paper.qmd
@@
 This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.
+
+For the analysis, we retrieved the following data as described in @tbl-use-var.
+
+| Variable | New Name   | Description                     | Example |
+|----------|------------|---------------------------------|---------|
+| sex      | sex        | Respondent's gender             | Female  |
+| age      | age        | Respondent's age                | 25      |
+| HEALTH   | health     | Respondents' health condition   | Good    |
+| SATHEALT | AGE        | The age of the respondents      | 23      |
+| PHYSHLTH | Phys_Health| Days of Respondents' physical health being not good   | 15    |
+| MNTLHLTH | Ment_Health| Respondents' mental health      | MALE    |
+
+: Source data retrieved from GSS {#tbl-use-var}
 

### 2024-03-28 paper/paper.qmd
Update readme on how to obtain data, and update the table on the paper

--- 2024-03-28 paper/paper.qmd
@@
 | Variable | New Name  | Description                   | Example |
-|----------|------------|---------------------------------|---------|
-| sex      | sex        | Respondent's gender             |2(FEMALE)|
-| HEALTH   | health     | The year of the survey recorded | 2007    |
-| SATHEALT | AGE        | The age of the respondents      | 23      |
-| PHYSHLTH | Phys_Health| Respondents' physical health    | MALE    |
+|----------|-----------|-------------------------------|---------|
+| sex      | sex       | Respondent's gender           | Female  |
+| age      | age       | Respondent's age              | 25      |
+| HEALTH   | health    | Respondents' health condition | Good    |
+| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
+| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
+| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |
 

### 2024-03-28 paper/paper.qmd
update references

--- 2024-03-28 paper/paper.qmd
@@
 
+This paper begins with an [Introduction] framing the impact of economic downturns on work hours.
+It is followed by the [Data] section detailing methodology and cleaning efforts.
+In the [Results], we analyze work hours and nonresponse rates, leading to the [Discussion] on labour market responses to crises, including the impact of COVID-19, and addressing ethical issues.
+We later acknowledge our paper's Limitations, suggest paths for Future Research, especially on enhancing response rates, and conclude with a synthesis of our insights.
+The [Appendix] provides further survey information.
+
 # Data {#sec-data}
@@
 | Variable | New Name  | Description                   | Example |
-|----------|------------|---------------------------------|---------|
-| sex      | sex        | Respondent's gender             | Female  |
-| age      | age        | Respondent's age                | 25      |
+|----------|-----------|-------------------------------|---------|
+| sex      | SEX       | Respondent's gender           | Female  |
+| age      | AGE       | Respondent's age              | 25      |
 | HEALTH   | health    | Respondents' health condition | Good    |
-| SATHEALT | AGE        | The age of the respondents      | 23      |
-| PHYSHLTH | Phys_Health| Respondents' physical health    | MALE    |
+| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
+| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
+| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |
 
@@
 ## Source Data
+The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
+The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
+One of the variable names `response` is renamed to be more informative (@tbl-use-var).
+
+The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].
+
+[^1]: https://gss.norc.org/documents/stata/GSS_stata.zip
 
 # Model
-
 The goal of our modelling strategy is twofold. Firstly,...

### 2024-03-31 paper/paper.qmd
update paper
redownload the raw data, updated the table of vairables in paper, and updated data_cleaning.R

@@
 |----------|-----------|-------------------------------|---------|
-| sex      | SEX       | Respondent's gender           | Female  |
-| age      | AGE       | Respondent's age              | 25      |
+| SEX      | sex       | Respondent's gender           | Female  |
+| AGE      | age       | Respondent's age              | 25      |
 | HEALTH   | health    | Respondents' health condition | Good    |
+| YEAR     | year      | Year of the Data Recorded     | 1977    |
 | PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
@@
 
-# Additional data details
+## Additional data details
 

### 2024-03-31 scripts/02-data_cleaning.R

@@ -50,6 +50,7 @@ read.dat <- function(dat, metadata_var, labels.included = "yes") {
   read.table(dat, col.names = metadata_var[["ColName"]])
 }
 
+
 GSS_metadata <- read.dct(here::here("data/raw_data/GSS.dct"))
 GSS_ascii <- read.dat(here::here("data/raw_data/GSS.dat"), GSS_metadata)
 attr(GSS_ascii, "col.label") <- GSS_metadata[["ColLabel"]]
@@ -59,6 +60,8 @@ GSS <- GSS_ascii
 #### Clean data ####
 # Actual Data cleaning
 
+# Select desired variables
+GSS <- select(GSS,c("ID_","YEAR","SEX","AGE","HEALTH","PHYSHLTH","MNTLHLTH","DEPRESS"))
 
 #### Save data ####
 write_parquet(GSS, here::here("data/analysis_data/cleaned_GSS.parquet"))

### 2024-03-31 paper/paper.qmd
Update and clean datasets for study

@@
 |----------|-----------|-------------------------------|---------|
+| ID_      | id        | Response ID                   | 1       |
+| YEAR     | year      | Year of the Data Recorded     | 1977    |
 | SEX      | sex       | Respondent's gender           | Female  |
@@
 | HEALTH   | health    | Respondents' health condition | Good    |
-| YEAR     | year      | Year of the Data Recorded     | 1977    |
 | PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |

### 2024-03-31 scripts/02-data_cleaning.R

@@ -10,6 +10,7 @@
 #### Workspace setup ####
 library(tidyverse)
 library(arrow)
+library(dplyr)
 
 #### Load data ####
 # This part of the code is from GSS Open Explore
@@ -60,8 +61,35 @@ GSS <- GSS_ascii
 #### Clean data ####
 # Actual Data cleaning
 
-# Select desired variables
+# Select desired variables and rename them for easier access/analyze 
 GSS <- select(GSS,c("ID_","YEAR","SEX","AGE","HEALTH","PHYSHLTH","MNTLHLTH","DEPRESS"))
+colnames(GSS) <- c("id","year","sex","age","health","phys_days","ment_days","depress")
+
+# Since we have non-responses due to the fact that many variables were only collected in
+# certain years, four separate datasets will be used for the paper.
+
+# 1. Dataset for demographic variables
+## Gender, Age, Numbers of days of Physical and Mental un-wellness. 
+demo_data <- filter(GSS, ment_days >= 0)
+demo_data <- select(demo_data,c("id","sex","age","phys_days","ment_days"))
+
+# 2. Dataset for the relationship between Numbers of days of Physical and Mental un-wellness
+days_data <- filter(GSS, ment_days >= 0) %>% filter(phys_days >= 0)
+days_data <- select(days_data,c("id","phys_days","ment_days"))
+
+# 3. Dataset for the relationship between whether diagnozed as having depression 
+# and Number of days of Physical un-wellness
+depress_data <- filter(GSS, phys_days >= 0) %>% filter(depress >= 0)
+depress_data <- select(depress_data,c("id","phys_days","depress"))
+
+# 4. Dataset for the relationship between Numbers of days of Mental un-wellness
+# and one's health status in general
+mentalVsHealth_data <- filter(GSS, ment_days >= 0) %>% filter(health >= 0)
+mentalVsHealth_data  <- select(mentalVsHealth_data,c("id","ment_days","health"))
 
 #### Save data ####
 write_parquet(GSS, here::here("data/analysis_data/cleaned_GSS.parquet"))
+write_parquet(demo_data, here::here("data/analysis_data/demo_data.parquet"))
+write_parquet(days_data, here::here("data/analysis_data/days_data.parquet"))
+write_parquet(depress_data, here::here("data/analysis_data/depress_data.parquet"))
+write_parquet(mentalVsHealth_data, here::here("data/analysis_data/mentalVsHealth_data.parquet"))

### 2024-03-31 scripts/01-download_data.R
updated readme and steps to download the data

@@ -1,26 +1,39 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Steps for Downloads and Saves the data from U.S. General Social Survey (GSS)
+# Author: Mingjia Chen
+# Date: March 31, 2024
+# Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: N/A
 
 #### Workspace setup ####
-library(opendatatoronto)
-library(tidyverse)
-# [...UPDATE THIS...]
+# No need for loading libraries 
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
+
+# Step 1: Visit the Website
+
+#The GSS data can be accessed through the NORC at the University of Chicago. Start by visiting the GSS website: https://gssdataexplorer.norc.org/MyGSS.
 
 
+# Step 2: Register
+
+#To download the GSS data, you are required to register an account. Follow the registration instructions provided on the GSS website.
+
+
+# Step 3: Locate the Relevant Variables to Extract from the GSS dataset
+
+# Once registered, you can access the datasets. 
+# The GSS website provides a search and filter function to help you find specific datasets.
+# Select the variable names "YEAR","SEX","AGE","HEALTH","PHYSHLTH","MNTLHLTH","DEPRESS" for extracting.
+
+
+# Step 4: Download the Data
+
+# After locating the relevant variables, the dataset can be downloaded. 
+# The GSS website offers data in various formats, Choose Excel Workbook (data + metadata) for replicating.
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 
+# No further action is required for saving data
          

### 2024-03-31 scripts/00-simulate_data.R
update simulate data and test cases

@@ -4,7 +4,7 @@
 # Date: 28 March 2024
 # Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: R
+# Pre-requisites: R 
 
 
 #### Workspace setup ####
@@ -13,20 +13,59 @@ library(tidyverse)
 #### Simulate data ####
 simulated_data <-
   tibble(
-    mental_health =runif(n = 1000,min = 0,max = 7) |> floor(),
-    physical_health = runif(n = 1000,min = 0,max = 7) |> floor(),
+    id = 1:1000,
+    year = runif(n = 1000, min = 1972, max = 2023) |> floor(),
+    sex = runif(n = 1000, min = 1, max = 3) |> floor(),
+    age = runif(n = 1000, min = 1, max = 100) |> floor(),
+    mental_health = runif(n = 1000,min = 0,max = 32) |> floor(),
+    physical_health = runif(n = 1000,min = 0,max = 32) |> floor(),
+    depress = runif(n = 1000, min = 1, max = 3) |> floor(),
+    health = runif(n = 1000, min = 1, max = 5) |> floor()
 )
 
-# expected that mental_health is only between 0 to 6
-# expected that  physical_health is only between 0 to 6
+# expected that id is only from 1 to 1000
+# expected that year is only from 1972 to 2022
+# expected that sex is only between 1 to 2
+# expected that age is only between 1 to 99
+# expected that mental_health is only between 0 to 31
+# expected that  physical_health is only between 0 to 31
+# expected that depress is only either 1 or 2
+# expected that health is only between 1 to 4
+
 
 #### Add tests for simulated data ####
 
-# expected that mental_health is only between 0 to 6
-any(unique(simulated_data$mental_health)) == c(0:6)
-min(simulated_data$mental_health) == 0
-max(simulated_data$mental_health) == 6
-# expected that  physical_health is only between 0 to 6
-any(unique(simulated_data$physical_health)) == c(0:6)
-min(simulated_data$physical_health) == 0
-max(simulated_data$physical_health) == 6
+# expected that id is only from 1 to 1000
+unique(simulated_data$id) == c(1:1000)
+
+# expected that year is only from 1972 to 2022
+max(simulated_data$year) <= 2022
+min(simulated_data$year) >= 1972
+
+# expected that sex is only between 1 to 2
+max(simulated_data$sex) == 2
+min(simulated_data$sex) == 1
[…]

### 2024-03-31 scripts/02-data_cleaning.R

@@ -70,7 +70,8 @@ colnames(GSS) <- c("id","year","sex","age","health","phys_days","ment_days","dep
 
 # 1. Dataset for demographic variables
 ## Gender, Age, Numbers of days of Physical and Mental un-wellness. 
-demo_data <- filter(GSS, ment_days >= 0)
+demo_data <- filter(GSS, ment_days >= 0) %>% filter(phys_days >= 0) %>% 
+  filter(age >= 1) %>% filter(sex >= 1)
 demo_data <- select(demo_data,c("id","sex","age","phys_days","ment_days"))
 
 # 2. Dataset for the relationship between Numbers of days of Physical and Mental un-wellness

### 2024-03-31 scripts/03-test_data.R

@@ -1,15 +1,65 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests for the four dataset cleaned to make sure it is suitable for analyses for the paper
+# Author: Mingjia Chen
+# Date: 31 March 2024
+# Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: cleaned_GSS.parquet, days_data.parquet, demo_data.parquet, depress_data.parquet, mentalVsMental_data.parquet
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(arrow)
+
+GSS <- read_parquet(here::here("data/analysis_data/cleaned_GSS.parquet"))
+demo_data <- read_parquet(here::here("data/analysis_data/demo_data.parquet"))
+days_data <- read_parquet(here::here("data/analysis_data/days_data.parquet"))
+depress_data <- read_parquet(here::here("data/analysis_data/depress_data.parquet"))
+mentalVsHealth <- read_parquet(here::here("data/analysis_data/mentalVsHealth_data.parquet"))
 
 #### Test data ####
+# expected that id is only from 1 to 72390
+unique(GSS$id) == c(1:72390)
+
+# expected that year is only from 1972 to 2022
+max(GSS$year) <= 2022
+min(GSS$year) >= 1972
+
+# expected that sex is only between 1 to 2
+max(demo_data$sex) == 2
+min(demo_data$sex) == 1
+### This test passed, but only after changing order and should be improved.
+any(unique(demo_data$sex) == c(2:1))
+
+# expected that age is only between 1 to 99
+min(demo_data$age) >= 1
+max(demo_data$age) <= 99
+
+# expected that mental_health is only between 0 to 31
+min(demo_data$ment_days) >= 0
+max(demo_data$ment_days) <= 31
+min(days_data$ment_days) >= 0
+max(days_data$ment_days) <= 31
+min(mentalVsHealth$ment_days) >= 0
+max(mentalVsHealth$ment_days) <= 31
+
+
+# expected that physical_health is only between 0 to 31
[…]

### 2024-03-31 paper/paper.qmd
modify cleanning data for analyses

@@
 author: 
-  - First author
-  - Another author
+  - Mingjia Chen
 thanks: "Code and data are available at: LINK."
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2)
+pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2,arrow)
 
@@
 library(ggplot2)
+library(arrow)
+
+#### Load data ####
+GSS <- read_parquet(here::here("data/analysis_data/cleaned_GSS.parquet"))
+demo_data <- read_parquet(here::here("data/analysis_data/demo_data.parquet"))
+days_data <- read_parquet(here::here("data/analysis_data/days_data.parquet"))
+depress_data <- read_parquet(here::here("data/analysis_data/depress_data.parquet"))
+mentalVsHealth <- read_parquet(here::here("data/analysis_data/mentalVsHealth_data.parquet"))
 ```
@@
 : Source data retrieved from GSS {#tbl-use-var}
+
+```{r}
+#| label: fig-demo-mental
+#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended
+#| fig-subcap: ["Gender","Age cohorts"]
+#| layout-ncol: 2
+#| echo: false
+#| warning: false
+#| message: false
+
+demo_data |>
+  ggplot(aes(x = ment_days, fill = sex)) +
+  geom_histogram(position = "dodge") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(
+    x = "Days of Feeling Unwell Mentally in Last 30 days",
+    y = "Occurrences",
+    fill = "Sex"
+  )
+
+demo_data |>
+  ggplot(aes(x = ment_days, fill = age_cohort)) +
+  geom_histogram(position = "dodge") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(
+    x = "Days of Feeling Unwell Mentally in Last 30 days",
+    y = "Occurrences",
+    fill = "Age Cohorts"
+  )
+
+```
+\break
+
+```{r}
+#| label: fig-demo-physical
+#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended
+#| fig-subcap: ["Gender","Age cohorts"]
+#| layout-ncol: 2
+#| echo: false
+#| warning: false
+#| message: false
+
+demo_data |>
+  ggplot(aes(x = phys_days, fill = sex)) +
+  geom_histogram(position = "dodge") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(
+    x = "Days of Feeling Unwell Physically in Last 30 days",
+    y = "Occurrences",
+    fill = "Sex"
+  )
+
+demo_data |>
+  ggplot(aes(x = phys_days, fill = age_cohort)) +
+  geom_histogram(position = "dodge") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(
+    x = "Days of Feeling Unwell Physically in Last 30 days",
+    y = "Occurrences",
+    fill = "Age Cohorts"
+  )
+
+```
+\break
 

### 2024-03-31 scripts/02-data_cleaning.R

@@ -74,6 +74,26 @@ demo_data <- filter(GSS, ment_days >= 0) %>% filter(phys_days >= 0) %>%
   filter(age >= 1) %>% filter(sex >= 1)
 demo_data <- select(demo_data,c("id","sex","age","phys_days","ment_days"))
 
+# change the sex variables from numbers to strings female and male
+demo_data$sex <- as.character(demo_data$sex)
+demo_data <- mutate(demo_data,
+               sex = case_when(
+                 sex == "1" ~ "Male",
+                 sex == "2" ~ "Female",
+                 TRUE ~ sex
+               )
+            )
+
+#categorize ages into five cohorts 
+#code referenced from https://pubs.wsb.wisc.edu/academics/analytics-using-r-2019/convert-numerical-data-to-categorical.html
+demo_data <- within(demo_data, {   
+  age_cohort <- NA # need to initialize variable
+  age_cohort[age < 20] <- "0-19"
+  age_cohort[age >= 20 & age < 40] <- "20-39"
+  age_cohort[age >= 40 & age < 60] <- "40-59"
+  age_cohort[age >= 60 & age < 80] <- "60-79"
+  age_cohort[age >= 80] <- "80+"
+} )
 # 2. Dataset for the relationship between Numbers of days of Physical and Mental un-wellness
 days_data <- filter(GSS, ment_days >= 0) %>% filter(phys_days >= 0)
 days_data <- select(days_data,c("id","phys_days","ment_days"))

### 2024-03-31 paper/paper.qmd
modify paper

@@
 
+## Source Data
+The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
+The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
+One of the variable names `response` is renamed to be more informative (@tbl-use-var).
+
 For the analysis, we retrieved the following data as described in @tbl-use-var.
@@
 : Source data retrieved from GSS {#tbl-use-var}
+
+## Data Cleaning
+
+The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].
+
+[^1]: https://gss.norc.org/documents/stata/GSS_stata.zip
+
+```{r}
+#| label: tbl-data-overview
+#| tbl-cap: Overview of the Categorized Data 
+#| echo: false
+#| warning: false
+#| message: false
+
+kable(demo_data,row.names = FALSE)|>
+  kable_styling() |>
+  row_spec(6, hline_after = TRUE)
+```
+
+## Survey Methodology
+
+some words
+
+## Demographic Variables
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+#categorize the range of days for visualizing the histogram of demographic variables
+
+demo_data <- within(demo_data, {   
+  ment_range <- NA # need to initialize variable
+  ment_range[ment_days < 10] <- "0-10"
+  ment_range[ment_days >= 10 & ment_days < 20] <- "10-20"
+  ment_range[ment_days >= 20 & ment_days < 30] <- "20-30"
+} )
+
+demo_data <- within(demo_data, {   
+  phys_range <- NA # need to initialize variable
+  phys_range[phys_days < 10] <- "0-10"
+  phys_range[phys_days >= 10 & phys_days < 20] <- "10-20"
+  phys_range[phys_days >= 20 & phys_days < 30] <- "20-30"
+} )
+```
 
@@
 \break
-
-## Source Data
-The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
-The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
-One of the variable names `response` is renamed to be more informative (@tbl-use-var).
-
-The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].
-
-[^1]: https://gss.norc.org/documents/stata/GSS_stata.zip
 

### 2024-03-31 paper/paper.qmd
update sub-data for model analysis

@@
 
-```{r}
-#| label: tbl-data-overview
-#| tbl-cap: Overview of the Categorized Data 
-#| echo: false
-#| warning: false
-#| message: false
-
-kable(demo_data,row.names = FALSE)|>
-  kable_styling() |>
-  row_spec(6, hline_after = TRUE)
-```
-
 ## Survey Methodology
@@
 ## Demographic Variables 
+```{r}
+#| label: tbl-data-overview
+#| tbl-cap: Overview of the Demographic Data 
+#| echo: false
+#| warning: false
+#| message: false
+
+vars <- c("ID","Gender","Age","Physical Unwellness","Mental Unwellness","Age Cohort")
+
+kable(head(demo_data), 
+      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Group", 
+      align = "c",
+      col.names = vars,
+      row.names = FALSE) |>
+  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+```
+
+## Demographic Variables
+
+# Model
+The goal of our modelling strategy is twofold. Firstly,...
+
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+
+## Model set-up
+
+Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+
+\begin{align} 
+y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_i + \gamma_i\\
+\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\beta &\sim \mbox{Normal}(0, 2.5) \\
+\gamma &\sim \mbox{Normal}(0, 2.5) \\
+\sigma &\sim \mbox{Exponential}(1)
+\end{align}
+
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+### Model justification
+
+We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+
+We can use maths by including latex between dollar signs, for instance $\theta$.
+
+# Results {#sec-results}
+
+Our results are summarized in @tbl-modelresults.
 
@@
 #| label: fig-demo-physical
-#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended
+#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended22
 #| fig-subcap: ["Gender","Age cohorts"]
@@
 \break
-
-# Model
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results {#sec-results}
-
-Our results are summarized in @tbl-modelresults.
 

### 2024-03-31 scripts/02-data_cleaning.R

@@ -100,8 +100,8 @@ days_data <- select(days_data,c("id","phys_days","ment_days"))
 
 # 3. Dataset for the relationship between whether diagnozed as having depression 
 # and Number of days of Physical un-wellness
-depress_data <- filter(GSS, phys_days >= 0) %>% filter(depress >= 0)
-depress_data <- select(depress_data,c("id","phys_days","depress"))
+analysis_data <- filter(GSS, phys_days >= 0) %>% filter(depress >= 0) %>% filter(ment_days >= 0)
+analysis_data <- select(analysis_data,c("id","phys_days","ment_days","depress"))
 
 # 4. Dataset for the relationship between Numbers of days of Mental un-wellness
 # and one's health status in general
@@ -112,5 +112,5 @@ mentalVsHealth_data  <- select(mentalVsHealth_data,c("id","ment_days","health"))
 write_parquet(GSS, here::here("data/analysis_data/cleaned_GSS.parquet"))
 write_parquet(demo_data, here::here("data/analysis_data/demo_data.parquet"))
 write_parquet(days_data, here::here("data/analysis_data/days_data.parquet"))
-write_parquet(depress_data, here::here("data/analysis_data/depress_data.parquet"))
+write_parquet(analysis_data, here::here("data/analysis_data/analysis_data.parquet"))
 write_parquet(mentalVsHealth_data, here::here("data/analysis_data/mentalVsHealth_data.parquet"))

### 2024-04-01 paper/paper.qmd
updated codes, cleanings, and more graphs for paper analyses

@@
 days_data <- read_parquet(here::here("data/analysis_data/days_data.parquet"))
-depress_data <- read_parquet(here::here("data/analysis_data/depress_data.parquet"))
+analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 mentalVsHealth <- read_parquet(here::here("data/analysis_data/mentalVsHealth_data.parquet"))
@@
 # Introduction {#sec-intro}
-
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
 
@@
 
-The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].
+The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].
 
@@
 ```{r}
-#| label: tbl-data-overview
+#| label: tbl-demo-overview
 #| tbl-cap: Overview of the Demographic Data 
@@
 kable(head(demo_data), 
-      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Group", 
+      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Groups", 
       align = "c",
@@
 
-## Demographic Variables
+## Mental and Physical Unwellness and Depression Diagnosis
+```{r}
+#| label: tbl-analysis-vars
+#| tbl-cap: Overview of the Main Analysis Dataset
+#| echo: false
+#| warning: false
+#| message: false
+
+vars <- c("ID","Physical Unwellness","Mental Unwellness","Depression Diagnosis")
+
+kable(head(analysis_data), 
+      caption = "Counted days of Physical and Mental unwellness with Depression Diagnosis", 
+      align = "c",
+      col.names = vars,
+      row.names = FALSE) |>
+  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+```
+
+## Mental Unwellness and General Health Status
+```{r}
+#| label: tbl-health-vars
+#| tbl-cap: Overview of the Mental Unwellness vs. General Health Status Dataset 
+#| echo: false
+#| warning: false
+#| message: false
+
+vars <- c("ID","Mental Unwellness","General Health")
+
+kable(head(mentalVsHealth), 
+      caption = "Counted days of Mental unwellness with General Health Status", 
+      align = "c",
+      col.names = vars,
+      row.names = FALSE) |>
+  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+```
+
+## Non-response Rate
+
+??? maybe include a table of non-response rate
+
+Some of the questions in the dataset are not included resulting no responses collected in certain years, while the other responses were collected.
+This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
+Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days is also included for only speculating these two variables.
+
+```{r}
+#| label: tbl-sub-vars
+#| tbl-cap: Overview of the Mental and Physical Unwellness
+#| echo: false
+#| warning: false
+#| message: false
+
+vars <- c("ID","Physical Unwellness","Mental Unwellness")
+
+kable(head(days_data), 
+      caption = "Counted days of Mental unwellness with General Health Status", 
+      align = "c",
+      col.names = vars,
+      row.names = FALSE) |>
+  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+```
 
@@
 
+## Depression Playing an Role
+```{r}
+#| label: fig-mental-vs-physical
+#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
+#| echo: false
+#| warning: false
+#| message: false
+
+#Modify depress status for visualization
+analysis_data$depress <- as.character(analysis_data$depress)
+analysis_data <- mutate(analysis_data,
+               depress = case_when(
+                 depress == "1" ~ "Yes",
+                 depress == "2" ~ "No",
+                 TRUE ~ depress
+               )
+            )
+
+#Graph
+analysis_data|>
+  ggplot(aes(x = ment_days, y = phys_days, color = depress)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  theme_minimal() +
+  labs(x = "Mental Unwellness", y = "Physical Unwellness", color = "Depress") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+\break
+
+## Mental Health and Health in General
+```{r}
+#| label: fig-mental-vs-general
+#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
+#| echo: false
+#| warning: false
+#| message: false
+
+#Graph
+mentalVsHealth|>
+  ggplot(aes(x = ment_days, y = health)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  theme_minimal() +
+  labs(x = "Mental Unwellness", y = "General Health") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+\break
+
+## Model Results
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+library(rstanarm)
+
+first_model <-
+  readRDS(file = here::here("models/first_model.rds"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+modelsummary::modelsummary(
+  list(
+    "First model" = first_model
+  ),
+  statistic = "mad",
+  fmt = 2
+)
+```
+
 # Discussion {#sec-discussion}
@@
 
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(first_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
 ## Diagnostics
@@
 
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+plot(first_model, "trace")
+
+plot(first_model, "rhat")
+```
+
 \newpage

### 2024-04-01 scripts/03-test_data.R

@@ -4,7 +4,7 @@
 # Date: 31 March 2024
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: cleaned_GSS.parquet, days_data.parquet, demo_data.parquet, depress_data.parquet, mentalVsMental_data.parquet
+# Pre-requisites: GSS.dct, GGS.dat, data_cleaning.R
 
 
 #### Workspace setup ####

### 2024-04-01 scripts/04-model.R

@@ -1,24 +1,24 @@
 #### Preamble ####
 # Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Mingjia Chen 
+# Date: 31 March 2024 
+# Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: GSS.dct, GGS.dat, data_cleaning.R
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
+    formula = phys_days ~ ment_days + depress,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-04-02 paper/paper.qmd
update graphs

@@
 ??? maybe include a table of non-response rate
+```{r}
+#| label: fig-nonresponse-rate
+#| fig-cap: Nonresponse Rates
+#| echo: false
+#| warning: false
+#| message: false
+
+# record number of non-responses in variables ment_days, phys_days, and depress
+no_response_data <- rep(0,3)
+
+#length(which(<condition>)) code referenced from https://www.geeksforgeeks.org/count-repeated-values-in-r/
+no_response_data <- c(length(which(GSS$phys_days<1)),length(which(GSS$ment_days<1)),length(which(GSS$depress<1)))
+
+# calculate the percentages
+total_responses <- nrow(GSS)
+non_response_rate <- no_response_data/total_responses
+questions <- c("Physical Unwellness","Mental Unwellness","Depression Status")
+non_response_data <- cbind(questions,non_response_rate)
+
+ggplot(non_response_data, aes(x = questions,y=non_response_rate)) +
+  geom_bar(stat = "identity",fill = "skyblue") +
+  theme_minimal() +
+  labs(title = "Non-Response Rates of each Question", x = "Questions", y = "Percentage of Non-Responses")
+
+```
 

### 2024-04-03 paper/paper.qmd
modify data cleaning for model purposes

@@
 
-This paper begins with an [Introduction] framing the impact of economic downturns on work hours.
-It is followed by the [Data] section detailing methodology and cleaning efforts.
-In the [Results], we analyze work hours and nonresponse rates, leading to the [Discussion] on labour market responses to crises, including the impact of COVID-19, and addressing ethical issues.
-We later acknowledge our paper's Limitations, suggest paths for Future Research, especially on enhancing response rates, and conclude with a synthesis of our insights.
+This paper begins with [Introduction] framing the impact of mental health on one's well being.
+The [Data] section details variables, methodology, and cleaning processes used for analyses.
+In [Model] section, a model is proposed for determining how individual's depression status and counted days of mental unwellness in the past 30 days impacts their counted days of physical unwellness in the past 30 days.
+[Results] section analyzes how demographic and other mental health related factors would affect physical health with model calculations.
+
+? Still need to fix this part
+[Discussion] section includes .
+We later acknowledge our paper's [Limitations], suggest paths for [Future Research], especially on enhancing response rates, and conclude with a synthesis of our insights.
 The [Appendix] provides further survey information.
@@
 The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
-One of the variable names `response` is renamed to be more informative (@tbl-use-var).
-
-For the analysis, we retrieved the following data as described in @tbl-use-var.
+The variable names are renamed to be more informative (@tbl-use-var).
 
@@
 | YEAR     | year      | Year of the Data Recorded     | 1977    |
-| SEX      | sex       | Respondent's gender           | Female  |
+| SEX      | sex       | Respondent's gender           | Female/2|
 | AGE      | age       | Respondent's age              | 25      |
@@
 | MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
-| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |
+| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes/1   |
 
@@
 
-??? maybe include a table of non-response rate
 ```{r}
@@
 non_response_rate <- no_response_data/total_responses 
+non_response_rate <- round(non_response_rate,3)
 questions <- c("Physical Unwellness","Mental Unwellness","Depression Status")
@@
 
-Some of the questions in the dataset are not included resulting no responses collected in certain years, while the other responses were collected.
+As shown in @fig-nonresponse-rate, some of the questions in the dataset are not included resulting no responses collected in certain years due to the change in survey methodology.
 This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
-Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days is also included for only speculating these two variables.
+Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
 
@@
 #| label: fig-demo-mental
-#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended
+#| fig-cap: Female Participants from 20 to 59 Years Old are More likely to Experience Mental Unwellness 
 #| fig-subcap: ["Gender","Age cohorts"]
@@
 #| label: fig-demo-physical
-#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended22
+#| fig-cap: Female Participants from 20 to 59 Years Old are More likely to Experience Physical Unwellness 
 #| fig-subcap: ["Gender","Age cohorts"]
@@
 
+Include some research about female having trouble due to medical racism etc. and possible reason why these age cohorts are more likely to experience both physical and mental unwellness.
+
 ## Depression Playing an Role
@@
 
-#Modify depress status for visualization
-analysis_data$depress <- as.character(analysis_data$depress)
-analysis_data <- mutate(analysis_data,
-               depress = case_when(
-                 depress == "1" ~ "Yes",
-                 depress == "2" ~ "No",
-                 TRUE ~ depress
-               )
-            )
-
 #Graph
-analysis_data|>
+graph_data|>
   ggplot(aes(x = ment_days, y = phys_days, color = depress)) +

### 2024-04-03 scripts/02-data_cleaning.R

@@ -102,6 +102,15 @@ days_data <- select(days_data,c("id","phys_days","ment_days"))
 # and Number of days of Physical un-wellness
 analysis_data <- filter(GSS, phys_days >= 0) %>% filter(depress >= 0) %>% filter(ment_days >= 0)
 analysis_data <- select(analysis_data,c("id","phys_days","ment_days","depress"))
+#Modify depress status for visualization
+analysis_data$depress <- as.character(analysis_data$depress)
+analysis_data <- mutate(analysis_data,
+                     depress = case_when(
+                       depress == "1" ~ "Yes",
+                       depress == "2" ~ "No",
+                       TRUE ~ depress
+                     )
+)
 
 # 4. Dataset for the relationship between Numbers of days of Mental un-wellness
 # and one's health status in general

### 2024-04-03 paper/paper.qmd
minor changes

@@
 | AGE      | age       | Respondent's age              | 25      |
-| HEALTH   | health    | Respondents' health condition | Good    |
+| HEALTH   | health    | Respondents' health condition | Good/2  |
 | PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
@@
 #Graph
-graph_data|>
+analysis_data|>
   ggplot(aes(x = ment_days, y = phys_days, color = depress)) +

### 2024-04-03 scripts/02-data_cleaning.R

@@ -13,7 +13,7 @@ library(arrow)
 library(dplyr)
 
 #### Load data ####
-# This part of the code is from GSS Open Explore
+# This part of the code is from GSS Open Explore (https://gssdataexplorer.norc.org/home)
 
 # When downloading the dataset from the website, the R script can be chosen to
 # be downloaded as well.

### 2024-04-03 paper/paper.qmd
introduction writing and updated reference list

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Mental Health Plays Significant Role in Physical Wellness"
+subtitle: "Intersectionality and Mental Illness Being Overlooked in the Medical Field"
 author: 
   - Mingjia Chen
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/MjChen120/Mental_to_Physical_Health.git."
 date: today
@@
 
-This paper begins with [Introduction] framing the impact of mental health on one's well being.
-The [Data] section details variables, methodology, and cleaning processes used for analyses.
-In [Model] section, a model is proposed for determining how individual's depression status and counted days of mental unwellness in the past 30 days impacts their counted days of physical unwellness in the past 30 days.
-[Results] section analyzes how demographic and other mental health related factors would affect physical health with model calculations.
+Mental health is one essential aspect of the general health of an individual and yet it is often overlooked in the past centuries.
+Mental illnesses are not only “silent diseases” of one’s mind, but could as well impact patients’ physical well-being in general [@Ohrnberger_Fichera_Sutton].
+As browsing through relevant journal articles, a question arises: could mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month?
 
-? Still need to fix this part
-[Discussion] section includes .
-We later acknowledge our paper's [Limitations], suggest paths for [Future Research], especially on enhancing response rates, and conclude with a synthesis of our insights.
+U.S.
+General Social Survey (GSS) data is used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions.
+The estimand is the difference in whether an individual could experience more occasions of feeling physically unwell if they have mental health unwellness versus not.
+This is considered in terms of those who were diagnosed as having depression by a doctor.
+
+The analysis of GSS data, including gender, age, and mental and physical health variables, seeks to provide detailed insights into how mental health issues impact physical unwellness, contributing to discussions on intersectionality and overlooked mental health in the medical field.
+
+<Results paragraph>
+
+This paper begins with [Introduction] framing the impact of mental health on one's well-being.
+The [Data] section details variables, methodology, and analysis cleaning processes.
+In the [Model] section, a model is proposed for determining how an individual's depression status and counted days of mental unwellness in the past 30 days impact their counted days of physical unwellness in the past 30 days.
+[Results] section analyzes how demographic and other mental health-related factors would affect physical health with model calculations, leading the [Discussion] section with gender intersectionality and mental health issues often being overlooked in the medical field.
+Limitations and Future Research sections are included for study limitations and future research directions.
 The [Appendix] provides further survey information.
@@
 The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@GSS].
-From the dataset, this paper focuses on the "number of hours worked last week" variable, from the years 1992 to 2022.
-This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.
+From the dataset, this paper focuses specifically on variables related to demographic backgrounds, mental health, and physical health, from 1992 to 2022.
+This longitudinal approach allows us to analyze whether an individual's demographic factors and mental health well-being could significantly contribute to their physical well-being.
 
 ## Source Data
+
 The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the number of days that an individual feel physically unwell in the past 30 days.
+Then $\beta_i$ is the number of days that this individual feel mentally unwell and $\gamma_i$ indicates whether the individual is diagnosed as depressive by a doctor.
+$y_i$ and $\beta_i$ are measured in days.
 
@@
 ### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
 

### 2024-04-15 paper/paper.qmd
update paper and preamble of the model.R script

@@
 ---
-title: "Mental Health Plays Significant Role in Physical Wellness"
-subtitle: "Intersectionality and Mental Illness Being Overlooked in the Medical Field"
+title: "Mental Health Plays Significant Role in Physical Wellnesss in 1972 to 2022 US General Social Surveys"
+subtitle: "Racial and Gender Unequity and Mental Illness Being Overlooked in the Medical Field"
 author: 
@@
 
-Mental health is one essential aspect of the general health of an individual and yet it is often overlooked in the past centuries.
+Mental health is one essential aspect of the general health of an individual and yet it is often overlooked.
 Mental illnesses are not only “silent diseases” of one’s mind, but could as well impact patients’ physical well-being in general [@Ohrnberger_Fichera_Sutton].
-As browsing through relevant journal articles, a question arises: could mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month?
+This paper examines whether mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month?
 
 U.S.
-General Social Survey (GSS) data is used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions.
+General Social Survey (GSS) data from 1972 to 2022 is used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions.
 The estimand is the difference in whether an individual could experience more occasions of feeling physically unwell if they have mental health unwellness versus not.
@@
 
-some words
+will be written
 
@@
 ```
+\break
 
@@
 ```
+
+\break
 
@@
 ### Model justification
+
+will be written
 
@@
 
+\break
+
 \newpage

### 2024-04-15 scripts/04-model.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
+# Purpose: Models created and prepared for studying whether reported days of mental unwellness in a month and being reported as having depression can have a impact on number of reported days of being physically unwell.
 # Author: Mingjia Chen 
 # Date: 31 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 

### 2024-04-15 paper/paper.qmd
update writings

@@
 title: "Mental Health Plays Significant Role in Physical Wellnesss in 1972 to 2022 US General Social Surveys"
-subtitle: "Racial and Gender Unequity and Mental Illness Being Overlooked in the Medical Field"
+subtitle: "Mental Illness Being Overlooked in the Medical Field with Racial and Gender Unequity"
 author: 
@@
 
-The analysis of GSS data, including gender, age, and mental and physical health variables, seeks to provide detailed insights into how mental health issues impact physical unwellness, contributing to discussions on intersectionality and overlooked mental health in the medical field.
+The analysis of GSS data, including gender, age, and mental and physical health variables, seeks to provide detailed insights into how mental health issues impact physical unwellness, contributing to discussions on intersectionality (complex sociological analytically framework for studying social and political identities resulted from unique combinations of discrimination and privilege) and overlooked mental health in the medical field.
 
@@
 
+Physical and mental health variables such as "health", "depress" status, and reported days of physical ("physhlth") and health ("mntlhlth") unwellness in a month are selected from GSS [@GSS] for main analysis.
+Variable "year" is chosen for checking data consistency and non-response rate over the years.
+Demographic data, specifically age and gender, were used as well for further analyses.
 The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
@@
 
+```{r}
+#| label: tbl-sub-vars
+#| tbl-cap: Overview of the Mental and Physical Unwellness
+#| echo: false
+#| warning: false
+#| message: false
+
+vars <- c("ID","Physical Unwellness","Mental Unwellness")
+
+kable(head(days_data), 
+      caption = "Counted days of Mental unwellness with General Health Status", 
+      align = "c",
+      col.names = vars,
+      row.names = FALSE) |>
+  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+```
+
 ## Survey Methodology
 
-will be written
+From 1992 until 2018, the General Social Survey (GSS) relied on face-to-face interviews to gather data.
+This method offered a robust data collection environment, allowing interviewers to delve deeper into responses and clarify any uncertainties.
+It provided an optimal means of gathering comprehensive data.
+However, in response to the COVID-19 Pandemic, between 2020 and 2021, the GSS transitioned primarily to web surveys for data collection.
+
+The GSS targeted English or Spanish-speaking adults aged 18 and above residing in US households [@GSS].
+This inclusive criteria aimed to attract a diverse pool of participants.
+Nevertheless, individuals falling outside this target demographic were deemed ineligible for the survey.
+Those who didn't speak English or Spanish or had mental and/or physical impediments preventing survey participation were considered outside the scope of the GSS [@GSS].
+
+Changes in the GSS's respondent selection process, such as modifications to the Kish grid methodology, present additional hurdles, potentially skewing the demographic representation of respondents.
+The move towards web-based surveys may have inadvertently excluded older demographics, who are typically less inclined to engage with online platforms, thus impacting the survey's demographic balance.
+This demographic shift is significant, as older populations may offer distinct perspectives, particularly concerning mental health issues.
+
+The survey queried participants with the questions, such as "Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good?" and "Now thinking about your physical health, which includes physical illness and injury, for how many days during the past 30 days was your physical health not good?" and expecting a response of number of days in a month.
+Significantly, between 1998 and 2022, the structure of the questions have consistently remained the same.
+This consistency in formatting ensures the data's stability, facilitating a high level of consistency for thorough analysis.
+The data consists of a combination of in-person, telephone, and web surveys.
 
 ## Demographic Variables
+
+Demographic variables such as gender and age are used to compare and contrast differences between population groups.
+To further analyze age, the continuous variable is categorized into cohorts "0-19","20-39","40-59","60-79", and "80+".
+Below attached an overview of the sub-dataset used for demographic analysis.
+
 ```{r}
@@
 ## Mental and Physical Unwellness and Depression Diagnosis
+
+One of the key variable used for further analysis is whether the respondent have been diagnosed as having depression by a doctor in the past.
+The survey used the question "Now I would like to ask you some questions about general health conditions.
+Has a doctor, nurse, or other health professional EVER told you that you had: D.
+Depression?" to collect a categorical response of "Yes" or "No".
+The variable is an external indication of respondents' mental health status, accompanying the main counted days variable that is used for the analysis.
+
 ```{r}
@@
 ## Mental Unwellness and General Health Status
+
+A variable collecting general health status is furthermore included for additional analyses.
+The variable is used as a supplementary tool indicating respondents' health in general to assist the analysis result.
+The question consists of four categorical responses by asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or  poor?"
+
 ```{r}
@@
 ## Non-response Rate
+
+To mitigate non-responses in the survey, the GSS implemented a technique known as subsampling for non-respondents.
+The core concept of subsampling entails selecting a subset of non-respondents and adjusting their weights to ensure an impartial design [@gssCodebook2014].
+This chosen subsample is then expanded to effectively mirror all non-respondents up to a predetermined cutoff date.
+By focusing resources on a more manageable subset of difficult cases for further follow-up, subsampling offers the potential to reduce both response error and non-response bias [@gssCodebook2014].
+
+The GSS's approach to managing non-responses underwent changes, notably in its recent iterations – specifically during the COVID-19 Pandemic.
+As web surveys were used in the 2021 survey, modifications were made to balance non-responses.
+Historically, the survey employed subsampling techniques to mitigate the impact of non-responses, ensuring a representative dataset.
+
+However, with the introduction of web-based surveys, new categories like "Skipped on Web" were introduced to categorize non-responses.
+This change raises questions about the comparability of data across years and the potential for increased non-response rates.
+Non-responses (@fig-nonresponse-rate) can significantly affect the analysis of physical and mental health status trends, particularly in capturing the full extent of respondents' health status.
+Furthermore, as mental health is a later introduced science compared to physical health and thus is not included in most of the previous surveys.
+Although survey data lack of mental health related questions is filtered out for analyses, it is important to take that fact into consideration.
 
@@
 ```
-\break
 
@@
 
-```{r}
-#| label: tbl-sub-vars
-#| tbl-cap: Overview of the Mental and Physical Unwellness
-#| echo: false
-#| warning: false
-#| message: false
-
-vars <- c("ID","Physical Unwellness","Mental Unwellness")
-
-kable(head(days_data), 
-      caption = "Counted days of Mental unwellness with General Health Status", 
-      align = "c",
-      col.names = vars,
-      row.names = FALSE) |>
-  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
-```
-
 \break
@@
 # Model
-The goal of our modelling strategy is twofold. Firstly,...
+Through the data analysis of the paper, a potential correlation between counted days of feeling mental and physical unwell is detected.
+To further analyze and estimate counted days of feeling physical unwell based on an individuals counted days of feeling mentally unwell and whether they were diagnosed as depressive in the past, a linear regression analysis is conducted.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
+## Mental Health and Health in General
+```{r}
+#| label: fig-mental-vs-general
+#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
+#| echo: false
+#| warning: false
+#| message: false
+
+#Graph
+mentalVsHealth|>
+  ggplot(aes(x = ment_days, y = health)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  theme_minimal() +
+  labs(x = "Mental Unwellness", y = "General Health") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+\break
+
 ## Depression Playing an Role
@@
 
-## Mental Health and Health in General
-```{r}
-#| label: fig-mental-vs-general
-#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
-#| echo: false
-#| warning: false
-#| message: false
+## Model Results
 
-#Graph
-mentalVsHealth|>
-  ggplot(aes(x = ment_days, y = health)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  theme_minimal() +
-  labs(x = "Mental Unwellness", y = "General Health") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
-```
-\break
-
-## Model Results
 ```{r}
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory models of counted days of physical unwellness based on counted days of mental unwellness and depression diagnosis"
 #| warning: false

### 2024-04-16 paper/paper.qmd
update paper

@@
 ---
-title: "Mental Health Plays Significant Role in Physical Wellnesss in 1972 to 2022 US General Social Surveys"
-subtitle: "Mental Illness Being Overlooked in the Medical Field with Racial and Gender Unequity"
+title: "Mental Health Plays Significant Role in Physical Wellness in 1972 to 2022 US General Social Surveys"
+subtitle: "Mental Illness Being Overlooked in the Medical Field with Gender Disparities"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Mental health is a relatively newly introduced topic in the field, but would mental health issues influence physical health as well?
+Focusing on numerous variables correlated to mental and physical health, this study uses data from the U.S.
+General Social Survey (GSS) from 1972 to 2022 to investigate the impact of mental health unwellness on physical health unwellness, focusing specifically on “reported days of feeling unwell in a month.” Our analysis reveals that mental unwellness leads to an increase in physical unwellness, and identifies disparities between demographic groups, with women disproportionately affected.
+These findings underscore the necessity for the importance of promoting mental health and supporting underrepresented groups in the medical field.."
 format: pdf
@@
 
+The estimand of the paper is the difference in whether an individual could experience more occasions of feeling physically unwell if they have mental health unwellness versus not.
+This is considered in terms of those who were diagnosed as having depression by a doctor.
 U.S.
-General Social Survey (GSS) data from 1972 to 2022 is used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions.
-The estimand is the difference in whether an individual could experience more occasions of feeling physically unwell if they have mental health unwellness versus not.
-This is considered in terms of those who were diagnosed as having depression by a doctor.
+General Social Survey (GSS) data from 1972 to 2022 is therefore used for this paper to examine whether the demographic and mental health-related factors as indicators of physical health conditions.
 
@@
 
-<Results paragraph>
+Findings in paper highlight significance on gender, sex, and counted days of feeling mentally unwell in terms of counted days of feeling physically unwell in a month.
+The effect of whether being diagnosed as having depression on physical health unwellness is not significant ($\beta_2$ = −1.43, p = .22), thus whether depression diagnosis have effect on physical unwellness is not evidence supported.
+On the other hand, counted days of feeling mentally unwell has a positive significant on counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
+This means that if an individual has 1 more day of feeling unwell mentally, they in general will report 0.27 more days when reporting number of days they feel physically unwell.
 
@@
 
-Physical and mental health variables such as "health", "depress" status, and reported days of physical ("physhlth") and health ("mntlhlth") unwellness in a month are selected from GSS [@GSS] for main analysis.
+Physical and mental health variables such as "health", "depress" status, and reported days of feeling physical ("physhlth") and health ("mntlhlth") unwell in a month are selected from GSS [@GSS] for main analysis.
 Variable "year" is chosen for checking data consistency and non-response rate over the years.
@@
 The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].
+Below in @tbl-sub-vars contains a snapshot of the main dataset being used for the purpose of analysis.
 
@@
 Demographic variables such as gender and age are used to compare and contrast differences between population groups.
-To further analyze age, the continuous variable is categorized into cohorts "0-19","20-39","40-59","60-79", and "80+".
+To further analyze age, as showcased in @tbl-demo-overview, the continuous variable is categorized into cohorts "0-19","20-39","40-59","60-79", and "80+".
 Below attached an overview of the sub-dataset used for demographic analysis.
@@
 Depression?" to collect a categorical response of "Yes" or "No".
-The variable is an external indication of respondents' mental health status, accompanying the main counted days variable that is used for the analysis.
+The variable is an external indication of respondents' mental health status, accompanying the main counted days variable that is used for the analysis (@tbl-analysis-vars).
 
@@
 
-A variable collecting general health status is furthermore included for additional analyses.
+A variable collecting general health status is furthermore included for additional analyses (@tbl-health-vars).
 The variable is used as a supplementary tool indicating respondents' health in general to assist the analysis result.
-The question consists of four categorical responses by asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or  poor?"
+The question consists of four categorical responses by asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or poor?" The respondants are expetced to choose one of the options to answer.
 
@@
 
-## Non-response Rate
+## Non-response Rate and Limitations
 
@@
 #| label: fig-nonresponse-rate
-#| fig-cap: Nonresponse Rates
+#| fig-cap: Nonresponse Rates - Responses for counted days of feeling physical unwell has the highest nonresponse rate
 #| echo: false
@@
   theme_minimal() +
-  labs(title = "Non-Response Rates of each Question", x = "Questions", y = "Percentage of Non-Responses")
+  labs(x = "Questions", y = "Proportion of Non-Responses")
 
@@
 Define $y_i$ as the number of days that an individual feel physically unwell in the past 30 days.
-Then $\beta_i$ is the number of days that this individual feel mentally unwell and $\gamma_i$ indicates whether the individual is diagnosed as depressive by a doctor.
-$y_i$ and $\beta_i$ are measured in days.
+Then $\beta_1$ is coefficient for the number of days that this individual feel mentally unwell and $\beta_2$ indicates the coefficient of whether the individual is diagnosed as depressive by a doctor.
+$y_i$ and days are measured in days.
 
@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\mu_i &= \beta_0 + \beta_1 days + \beta_2 diagnosis\\
 \beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
 \end{align}
@@
 
-will be written
+We anticipate that the counted days of feeling physical unwell would be closer to normal distribution, as different types of health-related factors would contribute to number of days people feeling unwell in a month; however, the relationship between days feeling unwell physically (dependent variable), days feeling unwell mentally (independent variable), and whether being diagnosed as having depression before (independent variable) is hypothesized to be linear.
+This is because we think feeling mentally unwell and having depression would contribute to higher possibility of feeling unwell physically, corresponding to our estimand.
+Due to the fact that these three questions were not included in all past surveys, only data that contains all three questions will be used for testifying the model.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+# Differences Detected betwen Demographic Populations
+
+To speculate possible demographic factors influencing days of feeling mental and physical unwell in a month, gender and sex are used.
+In general, female from 20 to 39 years old are more likely to report higher number of days feeling mentally unwell (@fig-demo-mental).
+In terms of physical health, female from 40 to 59 years old report higher number of days feeling unwell (@fig-demo-physical).
+
+As we can see, female in general report higher number of counted days of feeling both physical and mental unwellness in a month.
+The difference could be discrimination between gender groups, such as females usually being less represented in medical research.
+On the other hand, females are reported to be more sensitive to their mental health, that could be reason why they tend to have higher number of reports whether being mentally unwell.
 
@@
 #| label: fig-demo-mental
-#| fig-cap: Female Participants from 20 to 59 Years Old are More likely to Experience Mental Unwellness 
+#| fig-cap: Female Participants from 20 to 39 Years Old are More likely to Experience Mental Unwellness 
 #| fig-subcap: ["Gender","Age cohorts"]
@@
 #| label: fig-demo-physical
-#| fig-cap: Female Participants from 20 to 59 Years Old are More likely to Experience Physical Unwellness 
+#| fig-cap: Female Participants from 40 to 59 Years Old are More likely to Experience Physical Unwellness 
 #| fig-subcap: ["Gender","Age cohorts"]
@@
 
-Include some research about female having trouble due to medical racism etc. and possible reason why these age cohorts are more likely to experience both physical and mental unwellness.
+## Mental Health and Health in General
 
-## Mental Health and Health in General
+In addition to model and demographic analyses, an variable indicating respondents' general health was as well included for supplementary support of the paper.
+The general health variable is categorical, consisting four responses: "1" for Excellent, "2" for Good, "3" for Fair, and "4" for Poor.
+As shown in @fig-mental-vs-general, we can see that number of days feeling mentally unwell have a positive correlation with the general health status, meaning that if an individual has more days feeling mentally unwell, they are more likely to have poor general health as well.
+This result connects back to our estimand, supporting mental health's influence on one's physical health status.
+
 ```{r}
@@
 ## Depression Playing an Role
+
+With linear regression model analysis, result in @fig-mental-vs-physical shows that counted days of feeling mentally unwell is positively correlated to counted counted days of feeling physically unwell.
+The diagnosis of having depression has further positive effect on counted days of feeling physically unwell, making the correlation stronger.
+This result means that individuals with 1) higher counted days of feeling mentally unwell and 2) being diagnosed as having depression tend to report higher number of days feeling physically unwell.
+
+Based on @tbl-modelresults, however, although having influences on linear equation in @@fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = −1.43, p = .22).
+Counted days of feeling mentally unwell, on the other hand, do have significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
+Even though one of the correlation is not significant, it is still important for us to take the variable into consideration for possible future research.
+
 ```{r}
@@
 ```
-\break
-
-## Model Results
 

### 2024-04-17 paper/paper.qmd
update readme and paper

@@
 General Social Survey (GSS) from 1972 to 2022 to investigate the impact of mental health unwellness on physical health unwellness, focusing specifically on “reported days of feeling unwell in a month.” Our analysis reveals that mental unwellness leads to an increase in physical unwellness, and identifies disparities between demographic groups, with women disproportionately affected.
-These findings underscore the necessity for the importance of promoting mental health and supporting underrepresented groups in the medical field.."
+These findings underscore the necessity for the importance of promoting mental health and supporting underrepresented groups in the medical field."
 format: pdf
@@
 The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
+In total, 72390 responses (with 56% from female respondents) containing mentioned variables were collected.
 The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
@@
 : Source data retrieved from GSS {#tbl-use-var}
+
+```{r}
+#| label: tbl-sex
+#| tbl-cap: Number of Responses from Each Gender Group
+#| echo: false
+#| warning: false
+#| message: false
+
+genderdata <- filter(GSS, sex == 2)
+
+sex <- c("Male","Female")
+numbers <- c(nrow(genderdata), nrow(GSS)-nrow(genderdata))
+female_per <- round(nrow(genderdata)/nrow(GSS),2) * 100
+
+gendertable <- cbind(sex,numbers)
+kable(gendertable, 
+      align = "c",
+      row.names = FALSE,
+      col.names = c("Sex","Responses"))
+
+```
 
@@
 
+```{r}
+#| label: fig-countedDays
+#| tbl-cap: Number of Responses from Each Gender Group
+#| echo: false
+#| warning: false
+#| message: false
+
+```
 ## Survey Methodology
@@
 
-# Differences Detected betwen Demographic Populations
+## Differences Detected betwen Demographic Populations
 

### 2024-04-18 paper/paper.qmd
Update writing and literature

--- 2024-04-16 paper/paper.qmd
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2,arrow)
+pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2,arrow,ggpmisc)
 
@@
 library(arrow)
+library(ggpmisc)
 
@@
 Mental illnesses are not only “silent diseases” of one’s mind, but could as well impact patients’ physical well-being in general [@Ohrnberger_Fichera_Sutton].
-This paper examines whether mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month?
+This paper examines whether mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month.
 
@@
 
-The analysis of GSS data, including gender, age, and mental and physical health variables, seeks to provide detailed insights into how mental health issues impact physical unwellness, contributing to discussions on intersectionality (complex sociological analytically framework for studying social and political identities resulted from unique combinations of discrimination and privilege) and overlooked mental health in the medical field.
+The analysis of GSS data, including gender, age, and mental and physical health variables, seeks to provide detailed insights into how mental health issues impact physical unwellness, contributing to discussions on intersectionality (complex sociological analytical framework for studying social and political identities resulted from unique combinations of discrimination and privilege) and overlooked mental health in the medical field.
 
-Findings in paper highlight significance on gender, sex, and counted days of feeling mentally unwell in terms of counted days of feeling physically unwell in a month.
-The effect of whether being diagnosed as having depression on physical health unwellness is not significant ($\beta_2$ = −1.43, p = .22), thus whether depression diagnosis have effect on physical unwellness is not evidence supported.
-On the other hand, counted days of feeling mentally unwell has a positive significant on counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
-This means that if an individual has 1 more day of feeling unwell mentally, they in general will report 0.27 more days when reporting number of days they feel physically unwell.
+Findings in the paper highlight the significance of gender, sex, and counted days of feeling mentally unwell in terms of counted days of feeling physically unwell in a month.
+The effect of being diagnosed as having depression on physical health unwellness is not significant ($\beta_2$ = −1.43, p = .22), thus whether depression diagnosis affects physical unwellness is not evidence supported.
+On the other hand, counted days of feeling mentally unwell have a positive significance on counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
+This means that if an individual has 1 more day of feeling unwell mentally, they, in general, will report 0.27 more days when reporting the number of days they feel physically unwell.
 
@@
 
-Physical and mental health variables such as "health", "depress" status, and reported days of feeling physical ("physhlth") and health ("mntlhlth") unwell in a month are selected from GSS [@GSS] for main analysis.
+Physical and mental health variables such as "health", "depress" status, and reported days of feeling physical ("physhlth") and health ("mntlhlth") unwell in a month are selected from GSS [@GSS] for the main analysis.
 Variable "year" is chosen for checking data consistency and non-response rate over the years.
@@
 
-The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].
-Below in @tbl-sub-vars contains a snapshot of the main dataset being used for the purpose of analysis.
+The data was cleaned by using the open source statistical programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `ggpmisc` [@ggpmisc], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].
+Below in @tbl-sub-vars contains a snapshot of the main dataset being used for the purpose of analysis; two additional histograms (@fig-countedDays) are included as well, illustrating number of responses for each question.
+In general, most respondents have only a few or zero days of feeling both physically and mentally unwell in the past 30 days.
 
@@
 
+```{r}
+#| label: fig-countedDays
+#| fig-cap: Histograms for Number of Responses for Each Question
+#| fig-subcap: ["Mental Unwellness","Physical Unwellness"]
+#| layout-ncol: 2
+#| tbl-cap: Number for Each Responses 
+#| echo: false
+#| warning: false
+#| message: false
+
+demo_data |>
+  ggplot(aes(x = ment_days)) +
+  geom_histogram(position = "dodge") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(
+    x = "Days of Feeling Unwell Mentally in Last 30 days",
+    y = "Occurrences",
+    fill = "Sex"
+  )
+
+demo_data |>
+  ggplot(aes(x = phys_days)) +
+  geom_histogram(position = "dodge") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(
+    x = "Days of Feeling Unwell Physically in Last 30 days",
+    y = "Occurrences",
+    fill = "Age Cohorts"
+  )
+
+```
+
 ## Survey Methodology
@@
 
-The survey queried participants with the questions, such as "Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good?" and "Now thinking about your physical health, which includes physical illness and injury, for how many days during the past 30 days was your physical health not good?" and expecting a response of number of days in a month.
-Significantly, between 1998 and 2022, the structure of the questions have consistently remained the same.
+The survey queried participants with questions, such as "Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good?" and "Now thinking about your physical health, which includes physical illness and injury, for how many days during the past 30 days was your physical health not good?" and expecting a response of the number of days in a month.
+Significantly, between 1998 and 2022, the structure of the questions has consistently remained the same.
 This consistency in formatting ensures the data's stability, facilitating a high level of consistency for thorough analysis.
@@
 Demographic variables such as gender and age are used to compare and contrast differences between population groups.
-To further analyze age, as showcased in @tbl-demo-overview, the continuous variable is categorized into cohorts "0-19","20-39","40-59","60-79", and "80+".
-Below attached an overview of the sub-dataset used for demographic analysis.
+To further analyze age, as showcased in @tbl-demo-overview, the continuous variable is categorized into cohorts "0-19", "20-39", "40-59", "60-79", and "80+".
+Below is an overview of the sub-dataset used for demographic analysis.
+In total, as shown in @tbl-demoportion, 72390 responses (with 51% from female respondents and 44% from age cohort 40 to 59) containing mentioned variables were collected.
 
@@
 
+\break
+
+```{r}
+#| label: tbl-demoportion
+#| tbl-cap: Number of Responses from Each Demographic Group
+#| tbl-subcap: 
+#|   - "Sex"
+#|   - "Age Cohorts"
+#| layout-ncol: 2
+#| echo: false
+#| warning: false
+#| message: false
+
+genderdata <- filter(demo_data, sex == "Female")
+
+sex <- c("Male","Female","Total")
+numbers <- c(nrow(genderdata), nrow(demo_data)-nrow(genderdata),nrow(demo_data))
+female_per <- round(nrow(genderdata)/nrow(demo_data),2) * 100
+
+gendertable <- cbind(sex,numbers)
+kable(gendertable, 
+      align = "c",
+      row.names = FALSE,
+      col.names = c("Sex","Responses"))
+
+agetable <- count(demo_data, age_cohort)
+total <- c("Total",nrow(demo_data))
+agetable <- rbind(agetable,total)
+kable(agetable, 
+      align = "c",
+      row.names = FALSE,
+      col.names = c("Age Cohort","Responses"))
+age_per <- round(nrow(filter(demo_data,age_cohort == "40-59"))/nrow(demo_data),2) * 100
+```
+
+\break
+
 ## Mental and Physical Unwellness and Depression Diagnosis
 
-One of the key variable used for further analysis is whether the respondent have been diagnosed as having depression by a doctor in the past.
+One of the key variables used for further analysis is whether the respondent has been diagnosed as having depression by a doctor in the past.
 The survey used the question "Now I would like to ask you some questions about general health conditions.
@@
 The variable is used as a supplementary tool indicating respondents' health in general to assist the analysis result.
-The question consists of four categorical responses by asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or poor?" The respondants are expetced to choose one of the options to answer.
+The question consists of four categorical responses asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or poor?" The respondents are expected to choose one of the options to answer.
 
@@
 Non-responses (@fig-nonresponse-rate) can significantly affect the analysis of physical and mental health status trends, particularly in capturing the full extent of respondents' health status.
-Furthermore, as mental health is a later introduced science compared to physical health and thus is not included in most of the previous surveys.
-Although survey data lack of mental health related questions is filtered out for analyses, it is important to take that fact into consideration.
+Furthermore, mental health is a later introduced science compared to physical health and thus is not included in most of the previous surveys.
+Although survey data lack mental health-related questions filtered out for analyses, it is important to consider that fact.
 
@@
 #| label: fig-nonresponse-rate
-#| fig-cap: Nonresponse Rates - Responses for counted days of feeling physical unwell has the highest nonresponse rate
+#| fig-cap: Nonresponse Rates - Responses for counted days of feeling physically unwell have the highest nonresponse rate
 #| echo: false
@@
 
-As shown in @fig-nonresponse-rate, some of the questions in the dataset are not included resulting no responses collected in certain years due to the change in survey methodology.
-This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
-Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
-
 \break
 
+As shown in @fig-nonresponse-rate, some of the questions in the dataset are not included resulting in no responses collected in certain years due to the change in survey methodology.
+This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
+Hence, an additional sub-set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
+
 # Model
-Through the data analysis of the paper, a potential correlation between counted days of feeling mental and physical unwell is detected.
-To further analyze and estimate counted days of feeling physical unwell based on an individuals counted days of feeling mentally unwell and whether they were diagnosed as depressive in the past, a linear regression analysis is conducted.
+
+Through the data analysis of the paper, a potential correlation between counted days of feeling mentally and physically unwell is detected.
+To further analyze and estimate counted days of feeling physically unwell based on an individual's counted days of feeling mentally unwell and whether they were diagnosed as depressive in the past, a linear regression analysis is conducted.
 
@@
 
-Define $y_i$ as the number of days that an individual feel physically unwell in the past 30 days.
-Then $\beta_1$ is coefficient for the number of days that this individual feel mentally unwell and $\beta_2$ indicates the coefficient of whether the individual is diagnosed as depressive by a doctor.
+Define $y_i$ as the number of days that an individual felt physically unwell in the past 30 days.
+Then $\beta_1$ is the coefficient for the number of days that this individual felt mentally unwell and $\beta_2$ indicates the coefficient of whether the individual is diagnosed as depressive by a doctor.
 $y_i$ and days are measured in days.
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. Model justification and result will be explained later in this paper.
 
-### Model justification
+## Model justification
 
-We anticipate that the counted days of feeling physical unwell would be closer to normal distribution, as different types of health-related factors would contribute to number of days people feeling unwell in a month; however, the relationship between days feeling unwell physically (dependent variable), days feeling unwell mentally (independent variable), and whether being diagnosed as having depression before (independent variable) is hypothesized to be linear.
-This is because we think feeling mentally unwell and having depression would contribute to higher possibility of feeling unwell physically, corresponding to our estimand.
-Due to the fact that these three questions were not included in all past surveys, only data that contains all three questions will be used for testifying the model.
+We anticipate that the counted days of feeling physically unwell would be closer to a normal distribution, as different types of health-related factors would contribute to number of days people feeling unwell in a month; however, the relationship between days feeling unwell physically (dependent variable), days feeling unwell mentally (independent variable), and whether being diagnosed as having depression before (independent variable) is hypothesized to be linear.
+This is because we think feeling mentally unwell and having depression would contribute to a higher possibility of feeling unwell physically, corresponding to our estimand.
+Since these three questions were not included in all past surveys, only data that contains all three questions will be used for testifying the model.
 
@@
 
-# Differences Detected betwen Demographic Populations
+## Differences Detected between Demographic Populations
 
-To speculate possible demographic factors influencing days of feeling mental and physical unwell in a month, gender and sex are used.
-In general, female from 20 to 39 years old are more likely to report higher number of days feeling mentally unwell (@fig-demo-mental).
-In terms of physical health, female from 40 to 59 years old report higher number of days feeling unwell (@fig-demo-physical).
+To speculate possible demographic factors influencing days of feeling mentally and physically unwell in a month, gender and sex are used.
+In general, females from 20 to 39 years old are more likely to report a higher number of days feeling mentally unwell (@fig-demo-mental).
+In terms of physical health, females from 40 to 59 years old report a higher number of days of feeling unwell (@fig-demo-physical).
 
-As we can see, female in general report higher number of counted days of feeling both physical and mental unwellness in a month.
+As we can see, females in general report a higher number of counted days of feeling both physically and mentally unwellness in a month.
 The difference could be discrimination between gender groups, such as females usually being less represented in medical research.
-On the other hand, females are reported to be more sensitive to their mental health, that could be reason why they tend to have higher number of reports whether being mentally unwell.
+On the other hand, females are reported to be more sensitive to their mental health, which could be the reason why they tend to have a higher number of reports of being mentally unwell.
 
@@
 
-In addition to model and demographic analyses, an variable indicating respondents' general health was as well included for supplementary support of the paper.
-The general health variable is categorical, consisting four responses: "1" for Excellent, "2" for Good, "3" for Fair, and "4" for Poor.
-As shown in @fig-mental-vs-general, we can see that number of days feeling mentally unwell have a positive correlation with the general health status, meaning that if an individual has more days feeling mentally unwell, they are more likely to have poor general health as well.
+In addition to model and demographic analyses, a variable indicating respondents' general health was as well included for supplementary support of the paper.
+The general health variable is categorical, consisting of four responses: "1" for Excellent, "2" for Good, "3" for Fair, and "4" for Poor.
+As shown in @fig-mental-vs-general, we can see that the number of days feeling mentally unwell has a positive correlation with the general health status, meaning that if an individual has more days feeling mentally unwell, they are more likely to have poor general health as well.
 This result connects back to our estimand, supporting mental health's influence on one's physical health status.
@@
   geom_smooth(method = "lm") +
+  stat_poly_line() +
+  stat_poly_eq(use_label(c("eq", "R2"))) +
   theme_minimal() +
@@
 
-## Depression Playing an Role
+## Depression Playing a Role
 
-With linear regression model analysis, result in @fig-mental-vs-physical shows that counted days of feeling mentally unwell is positively correlated to counted counted days of feeling physically unwell.
-The diagnosis of having depression has further positive effect on counted days of feeling physically unwell, making the correlation stronger.
-This result means that individuals with 1) higher counted days of feeling mentally unwell and 2) being diagnosed as having depression tend to report higher number of days feeling physically unwell.
+With linear regression model analysis, the result in @fig-mental-vs-physical shows that counted days of feeling mentally unwell are positively correlated to counted days of feeling physically unwell.
+The diagnosis of depression has a further positive effect on counted days of feeling physically unwell, making the correlation stronger.
+This result means that individuals with 1) higher counted days of feeling mentally unwell and 2) being diagnosed as having depression tend to report a higher number of days feeling physically unwell.
 
-Based on @tbl-modelresults, however, although having influences on linear equation in @@fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = −1.43, p = .22).
-Counted days of feeling mentally unwell, on the other hand, do have significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
-Even though one of the correlation is not significant, it is still important for us to take the variable into consideration for possible future research.
+Based on @tbl-modelresults, however, although having influences on linear equation in @fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = −1.43, p = .22).
+Counted days of feeling mentally unwell, on the other hand, do have a significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
+Even though one of the correlation is not significant, it is still important for us to consider the variable for possible future research.
 
@@
 
+\break
+
 # Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+We find a positive correlation between mental and physical health, where depression diagnosis strengthens the correlation; on the other hand, we detect a disparity between gender groups, hinting at an association with the fact that females are underrepresented in the medical field.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Mental Health Issues Impact Physical Health {#sec-first-point}
 
-## Second discussion point
+## Influence by Depression Diagnosis
 
-## Third discussion point
+## Gender Disparity in Health
 
-## Weaknesses and next steps
+By comparing counted days of feeling mentally and physically unwell between different gender groups, we found that female respondents in general reported higher numbers of occasions feeling unwell.
+The trend could be a result of gender disparity in medical field, where women benefit less from medical research and advances because they are underrepresented as potential patients.
+The gender disparity in medical research, compounded by pervasive misogyny, translates into tangible disadvantages for female patients in real-world scenarios.
+From the literature review conducted by @Merone_Tsey_Russell_Nagle_2022, women continue to be significantly underrepresented in medical literature, with inadequate reporting and analysis of sex and gender in research and misogynistic perceptions persistently shape the narrative surrounding these issues.
+The result in this paper again highlights the disparity, reminding us that We still have a long way to acknowledge and solve gender and minority disparity problems in the research field.
 
-Weaknesses and next steps should also be included.
+## Weaknesses and Next Steps
 
@@
 
-## Additional data details
+## Survey Questions
 
-# Model details {#sec-model-details}
+\begin{enumerate}
+   \item What is your age group?
+   \begin{itemize}
+      \item Type in a Number
+      \item Not Applicable 
+   \end{itemize}
+   \item Please specify your gender:
+   \begin{enumerate}
+      \item Male
+      \item Female
+      \item Prefer not to say
+   \end{enumerate}
+   \item Would you say your own health, in general, is excellent, good, fair, or poor?
+   \begin{enumerate}
+      \item Excellent
+      \item Good
+      \item Fair
+      \item Poor
+      \item Not Applicable
+   \end{enumerate}
+   \item Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good?
+   \begin{itemize}
+      \item Type in a Number 
+      \item Not Applicable
+   \end{itemize}
+   \item Now thinking about your physical health, which includes physical illness and injury, for how many days during the past 30 days was your physical health not good?:
+   \begin{itemize}
+      \item Type in a Number 
+      \item Not Applicable
+   \end{itemize}
+   \item Now I would like to ask you some questions about general health conditions. Has a doctor, nurse, or other health professional EVER told you that you had Depression?
+   \begin{enumerate}
+      \item Yes
+      \item No
+      \item Not Applicable
+   \end{enumerate}
+\end{enumerate}
 
-## Posterior predictive check
+## Model details {#sec-model-details}
+
+### Posterior predictive check
 
@@
 
-## Diagnostics
+### Diagnostics
 
@@
 
-\break
-
 \newpage

### 2024-04-18 paper/paper.qmd
update discussions

@@
 Below is an overview of the sub-dataset used for demographic analysis.
-In total, as shown in @tbl-demoportion, 72390 responses (with 51% from female respondents and 44% from age cohort 40 to 59) containing mentioned variables were collected.
+In total, as shown in @tbl-demoportion, 9049 responses (with 51% from female respondents and 44% from age cohort 40 to 59) containing mentioned variables were collected.
 
@@
 \mu_i &= \beta_0 + \beta_1 days + \beta_2 diagnosis\\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
+\beta &\sim \mbox{Normal}(0, 2.5) 
 \end{align}
@@
 
+Corresponding to the results in the journal by @Ohrnberger_Fichera_Sutton, although not strong, the result of the paper supports the positive correlation between mental and physical health status ($\beta_1$ = 0.27, p = .01).
+The variables that are used for main analysis were only available in years 2002, 2006, 2010, 2014, 2018, and 2022 as mental health is a newly introduced concept in health science compared to physical health, hence the sample size (n = 9049) of our data may not accurately represent U.S.
+population in past decades.
+Moreover, mental health education may not be common, and even mistreated as a taboo, in the population at the time, causing individuals to dismiss mental discomfort.
+The correlation or impact thus could be strengthen by mental health promotions and educations in the future.
+
+In addition, counted days of feeling physically and mentally unwell might not fully capture an individual's health status for analysis, more relevant factors should be included for future analysis.
+Due to that reason, a variable capturing respondents' general health status was included for supplementary evidence.
+A positive correlation between counted days of mental unwellness and general health (@fig-mental-vs-general) was detected to further support our estimand.
+To elaborate, since the categorical variable is coded reversely (i.e.
+Excellent - 1 and Poor - 4), we can conclude that as the number of counted mental unwellness increases, the health status of that individual correspondingly worsens.
+
 ## Influence by Depression Diagnosis
+
+To support our estimand, an additional variable was added to indicate the respondents' depression diagnosis.
+From the graph (@fig-mental-vs-physical) and model (@tbl-modelresults) results, depression diagnosis contributes to increase the influence of mental unwellness to physical unwellness.
+Depression diagnosis, therefore, could be a positive moderator, which strengthens the relation between mental health (independent variable) and physical health (dependent variable).
+Other than depression diagnosis, other mental health issues have not been specifically speculated for the purpose of this particular study.
 
@@
 
-By comparing counted days of feeling mentally and physically unwell between different gender groups, we found that female respondents in general reported higher numbers of occasions feeling unwell.
+By comparing counted days of feeling mentally and physically unwell between different gender groups, we found that female respondents in general reported higher numbers of occasions feeling unwell (@fig-demo-mental and @fig-demo-physical).
 The trend could be a result of gender disparity in medical field, where women benefit less from medical research and advances because they are underrepresented as potential patients.
 The gender disparity in medical research, compounded by pervasive misogyny, translates into tangible disadvantages for female patients in real-world scenarios.
+
 From the literature review conducted by @Merone_Tsey_Russell_Nagle_2022, women continue to be significantly underrepresented in medical literature, with inadequate reporting and analysis of sex and gender in research and misogynistic perceptions persistently shape the narrative surrounding these issues.
@@
 ## Weaknesses and Next Steps
+
+There are many limitations and weakness in the analysis.
+For instance, counted days of feeling physically and mentally unwell in past 30 days might not fully capture an individual's mental and physical health status; although feeling unwell in a few days, the severity of the unwellness was not measured.
+An individual could feel seriously unwell physically or mentally, which could as well contribute to a factor for analyzing.
+On the other hand, no other mental health issues other than depression was being studied in the paper; different kinds of mental health issues could contributes to physical unwellness in different ways, further research could include those variables for a better narrative of the relationship.
+
+Not enough education on mental health could also influence variables we collected, based on the fact that the variables are collected in a self-report manner.
+Participants might reported inaccurate information due to not having mental health related knowledge.
+On the other hand, the disparity in gender and other minority groups could influence the variable validity as those groups are more likely to be underrepresented in medical research.
+There is still much room of improvements.
+
+With existing study and limitations, future studies could be conducted to improve and capture the relationship between mental and physical health more efficiently in the future.
 

### 2024-04-18 paper/paper.qmd
update paper and code stylying

@@
 
+As shown in @fig-nonresponse-rate, some of the questions in the dataset are not included resulting in no responses collected in certain years due to the change in survey methodology.
+This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
+Hence, an additional sub-set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
+
 ```{r}
@@
 
-\break
-
-As shown in @fig-nonresponse-rate, some of the questions in the dataset are not included resulting in no responses collected in certain years due to the change in survey methodology.
-This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
-Hence, an additional sub-set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
-
 # Model
@@
 \mu_i &= \beta_0 + \beta_1 days + \beta_2 diagnosis\\
-\beta &\sim \mbox{Normal}(0, 2.5) 
+\beta_i &\sim \mbox{Normal}(0, 2.5) \\
+\sigma &\sim \mbox{Exponential}(1)
 \end{align}
@@
 
+Lastly, by posterior predictive check, the posterior distribution indicates that the model is not doing a good job of fitting the data.
+The check result could be due to limitations of data mentioned above; furthermore, adding more relevant variables to the linear regression equation could as well improve the strength of the model.
+
 With existing study and limitations, future studies could be conducted to improve and capture the relationship between mental and physical health more efficiently in the future.
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior, we implement a posterior predictive check and compared the posterior with the prior.
+By definition, the posterior should be able to be used to simulate data similar to the actual data; however, the posterior simulated data barely recollect the characteristic of the dataset from GSS.
+This means that the model lack of strength in terms of the relationship.
+The weakness could be a result of data limitations mentioned in [Discussion].
 
@@
 #| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-cap: "The Model Fits Barely to the Data, Hinting A Weak Model for Explaining the circumstances"
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a trace plot.
+It shows lines bouncing around horizontally and have a nice overlap between the chains.
+@fig-stanareyouokay-2 is a Rhat plot.
+From the plot, $\hat{R} = 1.05$, which is very close to 1, and ideally no more than 1.1.
+These results suggest no problems in model we built for our paper.
 
@@
 \newpage
+\break
 

### 2024-04-18 scripts/00-simulate_data.R

@@ -4,7 +4,7 @@
 # Date: 28 March 2024
 # Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: R 
+# Pre-requisites: R
 
 
 #### Workspace setup ####
@@ -17,11 +17,11 @@ simulated_data <-
     year = runif(n = 1000, min = 1972, max = 2023) |> floor(),
     sex = runif(n = 1000, min = 1, max = 3) |> floor(),
     age = runif(n = 1000, min = 1, max = 100) |> floor(),
-    mental_health = runif(n = 1000,min = 0,max = 32) |> floor(),
-    physical_health = runif(n = 1000,min = 0,max = 32) |> floor(),
+    mental_health = runif(n = 1000, min = 0, max = 32) |> floor(),
+    physical_health = runif(n = 1000, min = 0, max = 32) |> floor(),
     depress = runif(n = 1000, min = 1, max = 3) |> floor(),
     health = runif(n = 1000, min = 1, max = 5) |> floor()
-)
+  )
 
 # expected that id is only from 1 to 1000
 # expected that year is only from 1972 to 2022
@@ -68,4 +68,3 @@ any(unique(simulated_data$depress) == c(1:2))
 max(simulated_data$health) <= 4
 min(simulated_data$health) >= 1
 any(unique(simulated_data$health) == c(1:4))
-

### 2024-04-18 scripts/01-download_data.R

@@ -1,29 +1,31 @@
 #### Preamble ####
-# Purpose: Steps for Downloads and Saves the data from U.S. General Social Survey (GSS)
+# Purpose: Steps for Downloads and Saves the data from U.S. GSS
 # Author: Mingjia Chen
 # Date: March 31, 2024
-# Contact: mingjia.chen@mail.utoronto.ca 
+# Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: N/A
 
 #### Workspace setup ####
-# No need for loading libraries 
+# No need for loading libraries
 
 #### Download data ####
 
 # Step 1: Visit the Website
 
-#The GSS data can be accessed through the NORC at the University of Chicago. Start by visiting the GSS website: https://gssdataexplorer.norc.org/MyGSS.
+#The GSS data can be accessed through the NORC at the University of Chicago.
+#Start by visiting the GSS website: https://gssdataexplorer.norc.org/MyGSS.
 
 
 # Step 2: Register
 
-#To download the GSS data, you are required to register an account. Follow the registration instructions provided on the GSS website.
+#To download the GSS data, you are required to register an account.
+#Follow the registration instructions provided on the GSS website.
 
 
 # Step 3: Locate the Relevant Variables to Extract from the GSS dataset
 
-# Once registered, you can access the datasets. 
+# Once registered, you can access the datasets.
 # The GSS website provides a search and filter function to help you find specific datasets.
 # Select the variable names "YEAR","SEX","AGE","HEALTH","PHYSHLTH","MNTLHLTH","DEPRESS" for extracting.
 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -11,9 +11,11 @@
 library(tidyverse)
 library(arrow)
 library(dplyr)
+library(foreign)
 
 #### Load data ####
-# This part of the code is from GSS Open Explore (https://gssdataexplorer.norc.org/home)
+# This part of the code is from GSS Open Explore
+# (https://gssdataexplorer.norc.org/home)
 
 # When downloading the dataset from the website, the R script can be chosen to
 # be downloaded as well.
@@ -21,7 +23,6 @@ library(dplyr)
 #After running this part of the code, the data will be available for modifying
 # and analyzing.
 
-library(foreign)
 read.dct <- function(dct, labels.included = "yes") {
   temp <- readLines(dct)
   temp <- temp[grepl("_column", temp)]
@@ -43,8 +44,8 @@ read.dct <- function(dct, labels.included = "yes") {
     out <- gsub("^\\s+|\\s+$", "", out)
     out <- gsub('\"', "", out, fixed = TRUE)
     class(out) <- classes[x] ; out }), NAMES)
-  temp_metadata[["ColName"]] <- make.names(gsub("\\s", "", temp_metadata[["ColName"]]))
-  temp_metadata
+    temp_metadata[["ColName"]] <- make.names(gsub("\\s", "", temp_metadata[["ColName"]]))
+    temp_metadata
 }
 
 read.dat <- function(dat, metadata_var, labels.included = "yes") {
@@ -61,18 +62,18 @@ GSS <- GSS_ascii
 #### Clean data ####
 # Actual Data cleaning
 
-# Select desired variables and rename them for easier access/analyze 
-GSS <- select(GSS,c("ID_","YEAR","SEX","AGE","HEALTH","PHYSHLTH","MNTLHLTH","DEPRESS"))
-colnames(GSS) <- c("id","year","sex","age","health","phys_days","ment_days","depress")
+# Select desired variables and rename them for easier access/analyze
+GSS <- select(GSS, c("ID_", "YEAR", "SEX", "AGE", "HEALTH", "PHYSHLTH", "MNTLHLTH", "DEPRESS"))
+colnames(GSS) <- c("id", "year", "sex", "age", "health", "phys_days", "ment_days", "depress")
 
 # Since we have non-responses due to the fact that many variables were only collected in
 # certain years, four separate datasets will be used for the paper.
 
 # 1. Dataset for demographic variables
-## Gender, Age, Numbers of days of Physical and Mental un-wellness. 
+## Gender, Age, Numbers of days of Physical and Mental un-wellness.
[…]

### 2024-04-18 scripts/03-test_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Tests for the four dataset cleaned to make sure it is suitable for analyses for the paper
+# Purpose: Tests for the four dataset cleaned to make sure it is suitable for analyses
 # Author: Mingjia Chen
 # Date: 31 March 2024
-# Contact: mingjia.chen@mail.utoronto.ca 
+# Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: GSS.dct, GGS.dat, data_cleaning.R
 
@@ -62,4 +62,3 @@ any(unique(depress_data$depress) == c(2:1))
 max(mentalVsHealth$health) <= 4
 min(mentalVsHealth$health) >= 1
 any(unique(mentalVsHealth$health) == c(1:4))
-

### 2024-04-18 scripts/04-model.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Models created and prepared for studying whether reported days of mental unwellness in a month and being reported as having depression can have a impact on number of reported days of being physically unwell.
-# Author: Mingjia Chen 
-# Date: 31 March 2024 
-# Contact: mingjia.chen@mail.utoronto.ca 
+# Purpose: Models created and prepared for the analysis in paper.
+# Author: Mingjia Chen
+# Date: 31 March 2024
+# Contact: mingjia.chen@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: GSS.dct, GGS.dat, data_cleaning.R
 
@@ -13,7 +13,8 @@ library(rstanarm)
 library(arrow)
 
 #### Read data ####
-analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
+path <- "data/analysis_data/analysis_data.parquet"
+analysis_data <- read_parquet(here::here(path))
 
 ### Model data ####
 first_model <-
@@ -33,5 +34,3 @@ saveRDS(
   first_model,
   file = "models/first_model.rds"
 )
-
-

### 2024-04-21 other/datasheet/datasheet.qmd
update datasheet

---
title: "Datasheet for U.S. General Social Survey (GSS) dataset"
author: 
  - Mingjia Chen
thanks: "Code and data are available at: https://github.com/MjChen120/Mental_to_Physical_Health.git."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

For the purpose of this tutorial, the hypothetical datasheet is constructed based on the textbook by @rohan and questions are extracted from @gebru2021datasheets, using open source statistically programming language R [@citeR]. The General Social Survey (GSS) dataset [@GSS], initiated by NORC at the University of Chicago and primarily funded by the National Science Foundation, has been diligently tracking societal shifts and studying the increasing intricacies of American culture since 1972.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The GSS stands as a vital national asset, publicly accessible and esteemed as one of the most extensively scrutinized repositories of data in the social sciences. NORC's commitment to broadening access to GSS data is exemplified through initiatives like the GSS Data Explorer, fostering utilization by legislators, policymakers, researchers, educators, and beyond.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - GSS is initiated by National Opinion Research Center (NORC) at the University of Chicago.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - GSS is primarily funded by the National Science Foundation (NSF).
4. *Any other comments?*
    - N/A

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Since 1972, the General Social Survey (GSS) has been conducting nationally representative surveys of adults in the United States. By gathering data on contemporary American society, the GSS aims to track and elucidate trends in opinions, attitudes, behaviors, social status, health status, and more. The GSS dataset focuses on collecting various data points from individuals to understand societal trends and patterns.
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are in general three types of instances in total: Likert scale, continuous, and categorical responses. The number of variables could not be listed here as GSS is a large social dataset, consisting of enorumous amount of variables.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset used for the research paper only contains a few variables from the original GSS data (larger set). The original GSS dataset is representative of the population as it collects responses from a high percentage of population; although having some degree in non-responsive rate, the data in recent decades should be representative to the population as huge amount of responses were collected without biases. 
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instances consist of raw data, where non-responses were transformed into number (for example, -100) that could be filtered out when analyzing. 
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Labels indicating the actual question asked and options offered to the respondents associated with each instance are included in the GSS Open Explorer for analysis purposes.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some information are missing from individual instances, this usually happened due to respondents' non-responding to certain questions or withdraw the survey.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- The number of counted days of felling mentally unwell and physically unwell in the past 30 days are made explicit, as we used linear regression analysis for evaluating the relationship between the numbers.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- N/A
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Due to the fact that the survery is in a self-report manner, errors such as biases, noises, or redundancies could take place in the dataset. They are not speculated in this particular research paper.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is extracted from GSS Open Explorer website; a) there is guarantees that they will exist, and remain constant, over time. 
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- TBD
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- TBD
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- TBD
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- TBD
16. *Any other comments?*
	- TBD

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-04-22 other/datasheet/datasheet.qmd
update datasheet

@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- The dataset is extracted from GSS Open Explorer website; a) there is guarantees that they will exist, and remain constant, over time. 
+	- The dataset is extracted from GSS Open Explorer website; a) there is guarantees that they will exist, and remain constant, over time since the dataset is created and maintained by NORC at University of Chicago with funding, b) official archival versions of the complete dataset, and c) there are restrictions associated with external resources that apply to a dataset consumer, such as GSS data can only be accessed from the Open Explorer and GSS dataset obtaining can be replicated with the same steps.
 11.
@@
 If so, please provide a description.*
-	- TBD
+	- The data is protected by legal privilege, as personal contents of individuals are not included in the data.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- TBD
+	- No.
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- TBD
+	- N/A
 14.
@@
 If so, please describe how.*
-	- TBD
+	- No it is not possible to indentify individuals.
 15.
@@
 If so, please provide a description.*
-	- TBD
+	- Some of the health data is contained that might be considered sensitive such as health status and mental illness diagnosis.
+In addition, demographic data such as gender and age are also included in the dataset.
 16. *Any other comments?*
-	- TBD
+	- N/A
 
@@
 If so, please describe how.*
-	- TBD
+	- From 1992 until 2018, the General Social Survey (GSS) relied on face-to-face interviews to gather data.
+In response to the COVID-19 Pandemic, between 2020 and 2021, the GSS transitioned primarily to web surveys for data collection.
 2.
@@
 How were these mechanisms or procedures validated?*
-	- TBD
+	- In person interview method offered a robust data collection environment, allowing interviewers to delve deeper into responses and clarify any uncertainties.
+It provided an optimal means of gathering comprehensive data.
+On the other hand, using online survey method allows GSS to collect larger amount of data with less effort required.
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- TBD
+	- N/A
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- TBD
+	- Americans in general were involved in the data collection process. The participants were not paid for the survey.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- TBD
+	- The data is collected from the year 1972 to 2022. This timeframe does match the creation timeframe of the data associated with the instances.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- N/A
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- TBD
+	- The data is obtained from GSS Open Data Explorer website, by selecting and extracting desired variables for studying.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- TBD
+	- Yes.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- TBD
+	- Yes.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- TBD
+	- N/A
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- In the paper, an analysis on non-response rates that could impact the dataset and its use on data subjects was conducted.
+The non-responese rates for each question were high.
+The rates could be influencing the representiveness of the dataset and the analysis.
 12. *Any other comments?*
-	- TBD
+	- N/A
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- Cleaning and relabeling of the data was done for 1) removing and processing the non-responses and 2) have variable names easier for understanding and replicating. 
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- The raw data was preproceesed with non-responses ahead of time for future uses.
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- https://github.com/MjChen120/Mental_to_Physical_Health/tree/main/scripts
 4. *Any other comments?*
-	- TBD
+	- N/A
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- The data have been used for numerous purposes for legislators, policymakers, researchers, educators, and beyond.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- One of my group project paper have used this dataset: https://github.com/MjChen120/Labour_Market_Resilience
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- Legislations, policy making, researching, and educating.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- N/A
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
+	- N/A
 6. *Any other comments?*
-	- TBD
+	- N/A
 
@@
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- The dataset is distributed on GSS Open Data Explorer.
 3. *When will the dataset be distributed?*
-	- TBD
+	- N/A
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- All contents of NORC websites is under NORC copyright protection: "No part of the contents of NORC websites may be reproduced, stored, or transmitted in any form or by any means, electronic or mechanical, in whole or in any part, without the express written consent of NORC.
+Requests for permissions should be directed to: commhelp@norc.org.
+“NORC” and associated graphic images are service marks of NORC and subject to United States and international trademark and other intellectual property protections." Link: https://gssdataexplorer.norc.org/terms_and_conditions
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- No.
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
+	- Yes.
+We are not supposed to include GSS raw data we used in the repository.
+For replicating with the raw dataset, users should follow our instructions to download the data from the Open Explorer website.
 7. *Any other comments?*
-	- TBD
+	- N/A
 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- National Opinion Research Center (NORC) at the University of Chicago.
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- commhelp@norc.org
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- No.
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- The dataset will be updated when research and new knowledge of labeling and instances are introduced at the time.
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- TBD
+	- No. All the dataset are avaliable from 1972 until now.
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- TBD
+	- Older versions of the dataset is still being hosted and maintained by having year labels on each variables and older variables used with descriptions ever appeared in the dataset. 
 7.
@@
 If so, please provide a description.*
-	- TBD
+	- No. Only NORC will be able to extend and conduct further survey to extend and build on the dataset. 
 8. *Any other comments?*
-	- TBD
+	- N/A
 

### 2024-04-22 paper/paper.qmd
update paper and title

@@
 ---
-title: "Mental Health Plays Significant Role in Physical Wellness in 1972 to 2022 US General Social Surveys"
+title: "Mental Health Plays Significant Role in Physical Wellness From 1972 to 2022 US General Social Surveys"
 subtitle: "Mental Illness Being Overlooked in the Medical Field with Gender Disparities"
@@
 Findings in the paper highlight the significance of gender, sex, and counted days of feeling mentally unwell in terms of counted days of feeling physically unwell in a month.
-The effect of being diagnosed as having depression on physical health unwellness is not significant ($\beta_2$ = −1.43, p = .22), thus whether depression diagnosis affects physical unwellness is not evidence supported.
-On the other hand, counted days of feeling mentally unwell have a positive significance on counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
+The effect of being diagnosed as having depression on physical health unwellness is not significant ($\beta_2$ = −1.43, p = .22), thus whether depression diagnosis affects physical unwellness is not supported by evidence.
+On the other hand, counted days of feeling mentally unwell have a significant positive influence on counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
 This means that if an individual has 1 more day of feeling unwell mentally, they, in general, will report 0.27 more days when reporting the number of days they feel physically unwell.
@@
 
-Physical and mental health variables such as "health", "depress" status, and reported days of feeling physical ("physhlth") and health ("mntlhlth") unwell in a month are selected from GSS [@GSS] for the main analysis.
+The source data was obtained from the public open website GSS Data Explorer[^1].
+The data was downloaded and filtered for the selected variables and further cleaning and relabeling was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
+The variable names are renamed to be more informative (@tbl-use-var).
+Physical and mental health variables such as "health", "depress" status, and reported days of feeling physically ("physhlth") and health ("mntlhlth") unwell in a month are selected from GSS [@GSS] for the main analysis.
 Variable "year" is chosen for checking data consistency and non-response rate over the years.
 Demographic data, specifically age and gender, were used as well for further analyses.
-The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
-The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
-The variable names are renamed to be more informative (@tbl-use-var).
 
@@
 
+[^1]: https://gssdataexplorer.norc.org/home
+
 ## Data Cleaning
@@
 Below in @tbl-sub-vars contains a snapshot of the main dataset being used for the purpose of analysis; two additional histograms (@fig-countedDays) are included as well, illustrating number of responses for each question.
-In general, most respondents have only a few or zero days of feeling both physically and mentally unwell in the past 30 days.
-
-[^1]: https://gss.norc.org/documents/stata/GSS_stata.zip
+In general, most respondents have only a few or zero days of feeling both physically and mentally unwell in the past 30 days, indicating the population in general well in mental and physical health.
 
@@
 #| label: fig-mental-vs-general
-#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
+#| fig-cap: Counts of Days Feeling Mentally Unwell in Last 30 Days Has Positive Correlation with Poor General Health.
 #| echo: false
@@
 #| label: fig-mental-vs-physical
-#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
+#| fig-cap: Counts of Days Feeling Mentally Unwell in Last 30 Days Has Positive Correlation with Counted Days of Feeling Physically Unwell, with Depression Diagnosis Affecting the Strength of the Correlation.
 #| echo: false
@@
 \newpage
-\break
 

### 2024-04-22 paper/paper.qmd
update paper and references

@@
 Mental illnesses are not only “silent diseases” of one’s mind, but could as well impact patients’ physical well-being in general [@Ohrnberger_Fichera_Sutton].
-This paper examines whether mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month.
+Further research analyses should be conducted to benefit people's health with statistical information, thus it is important to speculate the relationship in depth.
+Even though previous research evidence supports the relationship between mental and physical health, larger representative samples and additional health-related variables were not used.
+To contribute to the topic, this paper examines whether mental health-related and demographic factors impact the number of days an individual experiences physical unwellness in a month by using the U.S.
+General Social Survey (GSS) dataset.
 
@@
 The analysis of GSS data, including gender, age, and mental and physical health variables, seeks to provide detailed insights into how mental health issues impact physical unwellness, contributing to discussions on intersectionality (complex sociological analytical framework for studying social and political identities resulted from unique combinations of discrimination and privilege) and overlooked mental health in the medical field.
+The paper is essential to contribute to the narrative of the relationship between mental and physical health with the U.S.
+population dataset.
 
@@
 
-The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@GSS].
-From the dataset, this paper focuses specifically on variables related to demographic backgrounds, mental health, and physical health, from 1992 to 2022.
+The paper uses data collected from the US General Social Survey (GSS) from the National Opinion Research Center (NORC) at the University of Chicago [@GSS].
+From the dataset, this paper focuses specifically on variables related to demographic backgrounds, mental health, and physical health, from 1972 to 2022.
 This longitudinal approach allows us to analyze whether an individual's demographic factors and mental health well-being could significantly contribute to their physical well-being.
@@
 
-: Source data retrieved from GSS {#tbl-use-var}
+: Source data retrieved from GSS Data Explorer {#tbl-use-var}
 
@@
 
-The data was cleaned by using the open source statistical programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `ggpmisc` [@ggpmisc], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].
-Below in @tbl-sub-vars contains a snapshot of the main dataset being used for the purpose of analysis; two additional histograms (@fig-countedDays) are included as well, illustrating number of responses for each question.
-In general, most respondents have only a few or zero days of feeling both physically and mentally unwell in the past 30 days, indicating the population in general well in mental and physical health.
+The explained data was cleaned by using the open source statistical programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `ggpmisc` [@ggpmisc], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].
+Below in @tbl-sub-vars contains a snapshot of the main dataset being used for analysis; two additional histograms (@fig-countedDays) are included as well, illustrating the number of responses for each question.
+In general, most respondents have only a few or zero days of feeling both physically and mentally unwell in the past 30 days, indicating the population is generally well in mental and physical health.
+Very few responses were collected that fall in the ranges between 15 days to 20 days, and above 20 days and below 30 days.
+Remarkably, on the other hand, there are a certain amount of responses reporting 30 days, indicating percentages of participants experiencing high levels of health discomfort.
+The trends are similar between the two responses.
 
@@
 
-From 1992 until 2018, the General Social Survey (GSS) relied on face-to-face interviews to gather data.
+From 1972 until 2018, the General Social Survey (GSS) relied on face-to-face interviews to gather data.
 This method offered a robust data collection environment, allowing interviewers to delve deeper into responses and clarify any uncertainties.
@@
 The survey queried participants with questions, such as "Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good?" and "Now thinking about your physical health, which includes physical illness and injury, for how many days during the past 30 days was your physical health not good?" and expecting a response of the number of days in a month.
+The details of the questions used are listed in [Appendix -@sec-ques-details].
 Significantly, between 1998 and 2022, the structure of the questions has consistently remained the same.
@@
 Demographic variables such as gender and age are used to compare and contrast differences between population groups.
-To further analyze age, as showcased in @tbl-demo-overview, the continuous variable is categorized into cohorts "0-19", "20-39", "40-59", "60-79", and "80+".
+To further analyze age, as showcased in @tbl-demo-overview, the continuous variable is modified to be categorized into cohorts "0-19", "20-39", "40-59", "60-79", and "80+".
 Below is an overview of the sub-dataset used for demographic analysis.
-In total, as shown in @tbl-demoportion, 9049 responses (with 51% from female respondents and 44% from age cohort 40 to 59) containing mentioned variables were collected.
+In total, as shown in @tbl-demoportion, 9049 responses (with approximately 51% from female respondents and 44% from age cohort 40 to 59) containing mentioned variables were collected.
+Age cohort from 20 to 39 takes 43% of the responses; in other words, most respondents are from age 20 to 59 (87%).
 
@@
 
-One of the key variables used for further analysis is whether the respondent has been diagnosed as having depression by a doctor in the past.
+One of the key variables used for further analysis is whether the respondent has been diagnosed as having depression in the past.
 The survey used the question "Now I would like to ask you some questions about general health conditions.
 Has a doctor, nurse, or other health professional EVER told you that you had: D.
-Depression?" to collect a categorical response of "Yes" or "No".
+Depression?" to collect a categorical response of whether "Yes" or "No".
 The variable is an external indication of respondents' mental health status, accompanying the main counted days variable that is used for the analysis (@tbl-analysis-vars).
+About 21% of the participants have been diagnosed as having depression in the past.
+According to the Morbidity and Mortality Weekly Report from Centers for Diseases Control and Prevention (CDC) in U.S.[@CDControlPrevention_2023], 18.4% of U.S.
+adults reported having ever been diagnosed with depression during 2020.
+The percentage in dataset is slightly higher than weekly reports, which could be a result from error, sampling differences, and other factors.
 
@@
   kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+
+per <- round(count(filter(analysis_data,depress=="Yes")) / count(analysis_data), 2) * 100
 ```
@@
 
-## Survey Questions
+## Survey Questions {#sec-ques-details}
 

### 2024-04-23 paper/paper.qmd
update graph formatting and descriptions

@@
 
+\break
+
 ```{r}
 #| label: tbl-sub-vars
-#| tbl-cap: Overview of the Mental and Physical Unwellness
+#| tbl-cap: Counted days of Mental unwellness with General Health Status
 #| echo: false
@@
 kable(head(days_data), 
-      caption = "Counted days of Mental unwellness with General Health Status", 
       align = "c",
@@
 The survey queried participants with questions, such as "Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good?" and "Now thinking about your physical health, which includes physical illness and injury, for how many days during the past 30 days was your physical health not good?" and expecting a response of the number of days in a month.
-The details of the questions used are listed in [Appendix -@sec-ques-details].
+Further details of the questions used are listed in [Appendix -@sec-ques-details].
 Significantly, between 1998 and 2022, the structure of the questions has consistently remained the same.
@@
 #| label: tbl-demo-overview
-#| tbl-cap: Overview of the Demographic Data 
+#| tbl-cap: Counted days of Physical and Mental unwellness of Population by Age and Gender Groups
 #| echo: false
@@
 kable(head(demo_data), 
-      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Groups", 
       align = "c",
@@
 The variable is an external indication of respondents' mental health status, accompanying the main counted days variable that is used for the analysis (@tbl-analysis-vars).
-About 21% of the participants have been diagnosed as having depression in the past.
+From @tbl-analysis-depress, about 21% of the participants have been diagnosed as having depression in the past.
 According to the Morbidity and Mortality Weekly Report from Centers for Diseases Control and Prevention (CDC) in U.S.[@CDControlPrevention_2023], 18.4% of U.S.
@@
 #| label: tbl-analysis-vars
-#| tbl-cap: Overview of the Main Analysis Dataset
+#| tbl-cap: Counted days of Physical and Mental unwellness with Depression Diagnosis
 #| echo: false
@@
 kable(head(analysis_data), 
-      caption = "Counted days of Physical and Mental unwellness with Depression Diagnosis", 
       align = "c",
@@
 per <- round(count(filter(analysis_data,depress=="Yes")) / count(analysis_data), 2) * 100
+
+```
+\break
+```{r}
+#| label: tbl-analysis-depress
+#| tbl-cap: Distribution of Depression Diagnosis Responses
+#| echo: false
+#| warning: false
+#| message: false
+
+depresstable <- count(analysis_data, depress)
+total <- c("Total",nrow(analysis_data))
+depresstable <- rbind(depresstable ,total)
+kable(depresstable, 
+      align = "c",
+      row.names = FALSE,
+      col.names = c("Responses", "Occurrences"))
 ```
@@
 The question consists of four categorical responses asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or poor?" The respondents are expected to choose one of the options to answer.
+In @tbl-health-rep, number of occurrences for each responses are counted.
+Majority of the repspondents reported to have good (51%) or excellent (29%) health status.
 
@@
 
+per_good <- round(nrow(filter(mentalVsHealth, health == 2))/nrow(mentalVsHealth),2) * 100
+per_exc <- round(nrow(filter(mentalVsHealth, health == 1))/nrow(mentalVsHealth),2) * 100
+
 vars <- c("ID","Mental Unwellness","General Health")
-
 kable(head(mentalVsHealth), 
-      caption = "Counted days of Mental unwellness with General Health Status", 
       align = "c",
@@
   kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
+
+```
+
+```{r}
+#| label: tbl-health-rep
+#| tbl-cap: Distribution of General Health Responses
+#| echo: false
+#| warning: false
+#| message: false
+healthtable <- count(mentalVsHealth, health)
+total <- c("Total",nrow(mentalVsHealth))
+healthtable <- rbind(healthtable ,total)
+status <- data.frame(c("Excellent", "Good", "Fair", "Poor","Total"))
+colnames(status) <- c("Health Status")
+healthtable <- cbind(status, healthtable)
+kable(healthtable, 
+      align = "c",
+      row.names = FALSE,
+      col.names = c("Health Status", "Responses", "Occurrences"))
 ```
@@
 
-\newpage
-
 \appendix
@@
 ```
-
+\break
 ### Diagnostics
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-cap: "The convergence of the MCMC algorithm is checked for the model."
 #| fig-subcap: ["Trace plot", "Rhat plot"]

### 2024-04-23 paper/paper.qmd
fix result section

@@
 To speculate possible demographic factors influencing days of feeling mentally and physically unwell in a month, gender and sex are used.
-In general, females from 20 to 39 years old are more likely to report a higher number of days feeling mentally unwell (@fig-demo-mental).
+In general, most of the participants reported having less than 10 days of feeling unwell both mentally and physically.
+Throughout the responses except for 0 days, the occurrence of responses from female participants is higher than from male participants; this means that a larger percentage of female participants have experienced both mentally and physically unwell in the past 30 days.
+Age cohorts from 20 to 59 contribute to the majority of the occurrences for each response, which could be a result of the fact that the age cohort takes up to 87% of the dataset.
+In conclusion, females from 20 to 39 years old are more likely to report a higher number of days feeling mentally unwell (@fig-demo-mental).
 In terms of physical health, females from 40 to 59 years old report a higher number of days of feeling unwell (@fig-demo-physical).
@@
 As we can see, females in general report a higher number of counted days of feeling both physically and mentally unwellness in a month.
-The difference could be discrimination between gender groups, such as females usually being less represented in medical research.
+The difference could be disparity occurring between gender groups, such as females usually being less represented in medical research.
 On the other hand, females are reported to be more sensitive to their mental health, which could be the reason why they tend to have a higher number of reports of being mentally unwell.
@@
 
+## Nonresponse Rate
+
+As we illustrated in @fig-nonresponse-rate, non-response rates may also help indicate significant differences in participants' attitudes toward each question included in the survey.
+Physical health-related questions have the highest non-response rate, indicating that most of the participants lack the motivation to time on speculate their physical health.
+On the other hand, the non-response rate for mental health and depression diagnosis is lower than for physical health questions.
+This difference between non-response rates could show that participants are more likely to pay attention when they are feeling mentally unwell and are more willing to answer questions corresponding to mental health.
+
 ## Mental Health and Health in General
 
-In addition to model and demographic analyses, a variable indicating respondents' general health was as well included for supplementary support of the paper.
+In addition to model and demographic analyses, a variable indicating respondents' general health was also included for supplementary support of the paper.
 The general health variable is categorical, consisting of four responses: "1" for Excellent, "2" for Good, "3" for Fair, and "4" for Poor.
@@
 This result connects back to our estimand, supporting mental health's influence on one's physical health status.
+The relationship, however, is not strong ($\beta_1 =0.03$, $R^2 = 0.07$); this could be due to the fact that the health variable was not framed to be correlated to mental health.
+The variable may fail to associate with other health variables.
 
@@
 Counted days of feeling mentally unwell, on the other hand, do have a significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
-Even though one of the correlation is not significant, it is still important for us to consider the variable for possible future research.
+From @fig-mental-vs-physical, it is evident to state that depression diagnosis may be a moderator to strengthen the relationship between counted ays of mental and physical unwellness in the past 30 days.
+The lack of significance could be due to possible errors, validity of survey questions, biases, or other possible factors.
+Hence, even though one of the correlations is not significant, it is still important for us to consider the variable for possible future research.
 
@@
 
-## Weaknesses and Next Steps
+## Weaknesses
 
@@
 
+### Model Limitations
+
 Lastly, by posterior predictive check, the posterior distribution indicates that the model is not doing a good job of fitting the data.
 The check result could be due to limitations of data mentioned above; furthermore, adding more relevant variables to the linear regression equation could as well improve the strength of the model.
+
+## Future Directions
 

### 2024-04-23 paper/paper.qmd
Update Paper (Discussion) and a new research paper

@@
 
-We find a positive correlation between mental and physical health, where depression diagnosis strengthens the correlation; on the other hand, we detect a disparity between gender groups, hinting at an association with the fact that females are underrepresented in the medical field.
+For the main anlysis, we find a positive correlation between mental and physical health, where depression diagnosis strengthens the correlation; on the other hand, we detect a disparity between gender groups, hinting at an association with the fact that females are underrepresented in the medical field.
 
@@
 Corresponding to the results in the journal by @Ohrnberger_Fichera_Sutton, although not strong, the result of the paper supports the positive correlation between mental and physical health status ($\beta_1$ = 0.27, p = .01).
-The variables that are used for main analysis were only available in years 2002, 2006, 2010, 2014, 2018, and 2022 as mental health is a newly introduced concept in health science compared to physical health, hence the sample size (n = 9049) of our data may not accurately represent U.S.
+Many possible reasons can contribute to the result we have for the paper.
+The variables that are used for the main analysis were only available in the years 2002, 2006, 2010, 2014, 2018, and 2022 since mental health is a newly introduced concept in health science compared to physical health, hence the sample size (n = 9049) of our data may not accurately represent U.S.
 population in past decades.
-Moreover, mental health education may not be common, and even mistreated as a taboo, in the population at the time, causing individuals to dismiss mental discomfort.
-The correlation or impact thus could be strengthen by mental health promotions and educations in the future.
+Moreover, mental health education may not be common, and even mistreated as a taboo, to the society at the time, causing individuals to dismiss their mental discomfort or issues.
+Participants might refuse to answer relevant questions because they are afraid of discrimination as those personal health variables could make them vulnerable to social rejection.
+The correlation or impact thus could be strengthened by mental health promotions and education in the future: having a society that promotes and educates mental health, participants have better knowledge of their own health status and more responses recollecting the accurate status will be available for analysis.
 
@@
 Excellent - 1 and Poor - 4), we can conclude that as the number of counted mental unwellness increases, the health status of that individual correspondingly worsens.
+Keep in mind that the strength of the correlation is not strong, but the result provides an insight of how mental health issues could influence health in general.
 
@@
 
-To support our estimand, an additional variable was added to indicate the respondents' depression diagnosis.
+Research [@Trivedi_the_Link_2004] indicate that physical symptoms frequently accompany depression, with vague aches and pains often being the primary indicators.
+These symptoms commonly manifest as chronic joint pain, limb discomfort, backaches, gastrointestinal issues, fatigue, sleep disturbances, alterations in psychomotor activity, and changes in appetite.
+A significant portion of patients initially seek medical attention solely for physical complaints, only to later discover a diagnosis of depression.
+Reseaches provide an insight that mental health issues are often associated with physical symptoms.
+Thus, to support our estimand, an additional variable was added to indicate the respondents' depression diagnosis.
 From the graph (@fig-mental-vs-physical) and model (@tbl-modelresults) results, depression diagnosis contributes to increase the influence of mental unwellness to physical unwellness.
-Depression diagnosis, therefore, could be a positive moderator, which strengthens the relation between mental health (independent variable) and physical health (dependent variable).
-Other than depression diagnosis, other mental health issues have not been specifically speculated for the purpose of this particular study.
+Depression diagnosis, therefore, could be a moderator, which strengthens the relation between mental health (independent variable) and physical health (dependent variable).
+Other than depression diagnosis, no additional mental health issues are speculated for the purpose of this particular study.
+The result with GSS dataset, alothough not significant, support the fact that depression plays an role in impacting physical health.
 
@@
 
-## Weaknesses
+## Weaknesses and Future Directions
 
@@
 
-Not enough education on mental health could also influence variables we collected, based on the fact that the variables are collected in a self-report manner.
-Participants might reported inaccurate information due to not having mental health related knowledge.
+As mentioned before, the variables that are used for the main analysis were only available in the years 2002, 2006, 2010, 2014, 2018, and 2022; the gap between years in the dataset fails to illustrate the trends as its narrative lacks data from the other years.
+Moreover, not enough education on mental health could also influence the variables we collected, based on the fact that the variables are collected in a self-report manner.
+Participants might report inaccurate information due to not having mental health-related knowledge.
 On the other hand, the disparity in gender and other minority groups could influence the variable validity as those groups are more likely to be underrepresented in medical research.
-There is still much room of improvements.
-
-### Model Limitations
+There is still much room for improvement.
 
@@
 
-## Future Directions
-
-With existing study and limitations, future studies could be conducted to improve and capture the relationship between mental and physical health more efficiently in the future.
+There are still many mental and physical health factors that we did not touch on to study their relationship in deeper depth.
+With existing studies and limitations concluded, future studies could be conducted to improve and capture the relationship between mental and physical health more efficiently in the future.
 

### 2024-04-23 paper/paper.qmd
final check + fix typos

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2,arrow,ggpmisc)
+pacman::p_load(janitor, here, dplyr, tidyverse, knitr, kableExtra, ggplot2, arrow, ggpmisc)
 
@@
 
-\break
-
 ```{r}
@@
 
-vars <- c("ID","Physical Unwellness","Mental Unwellness")
+vars <- c("ID", "Physical Unwellness", "Mental Unwellness")
 
@@
 #| fig-cap: Histograms for Number of Responses for Each Question
-#| fig-subcap: ["Mental Unwellness","Physical Unwellness"]
+#| fig-subcap: ["Mental Unwellness", "Physical Unwellness"]
 #| layout-ncol: 2
-#| tbl-cap: Number for Each Responses 
 #| echo: false
@@
 
-vars <- c("ID","Gender","Age","Physical Unwellness","Mental Unwellness","Age Cohort")
+vars <- c("ID", "Gender", "Age", "Physical Unwellness", "Mental Unwellness", "Age Cohort")
 
@@
 
-sex <- c("Male","Female","Total")
-numbers <- c(nrow(genderdata), nrow(demo_data)-nrow(genderdata),nrow(demo_data))
+sex <- c("Male", "Female", "Total")
+numbers <- c(nrow(genderdata), nrow(demo_data)-nrow(genderdata), nrow(demo_data))
 female_per <- round(nrow(genderdata)/nrow(demo_data),2) * 100
@@
       row.names = FALSE,
-      col.names = c("Sex","Responses"))
+      col.names = c("Sex", "Responses"))
 
@@
       row.names = FALSE,
-      col.names = c("Age Cohort","Responses"))
-age_per <- round(nrow(filter(demo_data,age_cohort == "40-59"))/nrow(demo_data),2) * 100
+      col.names = c("Age Cohort", "Responses"))
+
+age_per <- round(nrow(filter(demo_data,age_cohort == "40-59"))/nrow(demo_data), 2) * 100
 ```
@@
 From @tbl-analysis-depress, about 21% of the participants have been diagnosed as having depression in the past.
-According to the Morbidity and Mortality Weekly Report from Centers for Diseases Control and Prevention (CDC) in U.S.[@CDControlPrevention_2023], 18.4% of U.S.
-adults reported having ever been diagnosed with depression during 2020.
-The percentage in dataset is slightly higher than weekly reports, which could be a result from error, sampling differences, and other factors.
+According to the Morbidity and Mortality Weekly Report from the Centers for Disease Control and Prevention (CDC) in the U.S.[@CDControlPrevention_2023], 18.4% of U.S.
+adults reported having ever been diagnosed with depression in 2020.
+The percentage in dataset is slightly higher than weekly reports, which could be a result of error, sampling differences, and other factors.
 
@@
 
-vars <- c("ID","Physical Unwellness","Mental Unwellness","Depression Diagnosis")
+vars <- c("ID", "Physical Unwellness", "Mental Unwellness", "Depression Diagnosis")
 
@@
 
-per <- round(count(filter(analysis_data,depress=="Yes")) / count(analysis_data), 2) * 100
+per <- round(count(filter(analysis_data, depress=="Yes")) / count(analysis_data), 2) * 100
 
@@
 total <- c("Total",nrow(analysis_data))
-depresstable <- rbind(depresstable ,total)
+depresstable <- rbind(depresstable, total)
 kable(depresstable, 
@@
 The question consists of four categorical responses asking the respondents: "Would you say your own health, in general, is excellent, good, fair, or poor?" The respondents are expected to choose one of the options to answer.
-In @tbl-health-rep, number of occurrences for each responses are counted.
-Majority of the repspondents reported to have good (51%) or excellent (29%) health status.
+In @tbl-health-rep, the number of occurrences for each response is counted.
+The majority of the respondents reported to have good (51%) or excellent (29%) health status.
 
@@
 
-vars <- c("ID","Mental Unwellness","General Health")
+vars <- c("ID", "Mental Unwellness", "General Health")
 kable(head(mentalVsHealth), 
@@
 healthtable <- count(mentalVsHealth, health)
-total <- c("Total",nrow(mentalVsHealth))
-healthtable <- rbind(healthtable ,total)
+total <- c("Total", nrow(mentalVsHealth))
+healthtable <- rbind(healthtable, total)
 status <- data.frame(c("Excellent", "Good", "Fair", "Poor","Total"))
@@
 This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added.
-Hence, an additional sub-set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
+Hence, an additional subset of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.
 
@@
 #length(which(<condition>)) code referenced from https://www.geeksforgeeks.org/count-repeated-values-in-r/
-no_response_data <- c(length(which(GSS$phys_days<1)),length(which(GSS$ment_days<1)),length(which(GSS$depress<1)))
+no_response_data <- c(length(which(GSS$phys_days<1)), length(which(GSS$ment_days<1)), length(which(GSS$depress<1)))
 
@@
 non_response_rate <- no_response_data/total_responses 
-non_response_rate <- round(non_response_rate,3)
-questions <- c("Physical Unwellness","Mental Unwellness","Depression Status")
-non_response_data <- cbind(questions,non_response_rate)
+non_response_rate <- round(non_response_rate, 3)
+questions <- c("Physical Unwellness", "Mental Unwellness", "Depression Status")
+non_response_data <- cbind(questions, non_response_rate)
 
-ggplot(non_response_data, aes(x = questions,y=non_response_rate)) +
-  geom_bar(stat = "identity",fill = "skyblue") +
+ggplot(non_response_data, aes(x = questions, y=non_response_rate)) +
+  geom_bar(stat = "identity", fill = "skyblue") +
   theme_minimal() +
@@
 #| label: fig-demo-mental
-#| fig-cap: Female Participants from 20 to 39 Years Old are More likely to Experience Mental Unwellness 
-#| fig-subcap: ["Gender","Age cohorts"]
+#| fig-cap: Female Participants from 20 to 39 Years Old are More Likely to Experience Mental Unwellness 
+#| fig-subcap: ["Gender", "Age cohorts"]
 #| layout-ncol: 2
@@
 #| label: fig-demo-physical
-#| fig-cap: Female Participants from 40 to 59 Years Old are More likely to Experience Physical Unwellness 
-#| fig-subcap: ["Gender","Age cohorts"]
+#| fig-cap: Female Participants from 40 to 59 Years Old are More Likely to Experience Physical Unwellness 
+#| fig-subcap: ["Gender", "Age cohorts"]
 #| layout-ncol: 2
@@
 
-For the main anlysis, we find a positive correlation between mental and physical health, where depression diagnosis strengthens the correlation; on the other hand, we detect a disparity between gender groups, hinting at an association with the fact that females are underrepresented in the medical field.
+For the main analysis, we find a positive correlation between mental and physical health, where depression diagnosis strengthens the correlation; on the other hand, we detect a disparity between gender groups, hinting at an association with the fact that females are underrepresented in the medical field.
 
@@
 Excellent - 1 and Poor - 4), we can conclude that as the number of counted mental unwellness increases, the health status of that individual correspondingly worsens.
-Keep in mind that the strength of the correlation is not strong, but the result provides an insight of how mental health issues could influence health in general.
+Keep in mind that the strength of the correlation is not strong, but the result provides insight into how mental health issues could influence health in general.
 
@@
 
-Research [@Trivedi_the_Link_2004] indicate that physical symptoms frequently accompany depression, with vague aches and pains often being the primary indicators.
+Research [@Trivedi_the_Link_2004] indicates that physical symptoms frequently accompany depression, with vague aches and pains often being the primary indicators.
 These symptoms commonly manifest as chronic joint pain, limb discomfort, backaches, gastrointestinal issues, fatigue, sleep disturbances, alterations in psychomotor activity, and changes in appetite.
 A significant portion of patients initially seek medical attention solely for physical complaints, only to later discover a diagnosis of depression.
-Reseaches provide an insight that mental health issues are often associated with physical symptoms.
+Research provides an insight that mental health issues are often associated with physical symptoms.
 Thus, to support our estimand, an additional variable was added to indicate the respondents' depression diagnosis.
-From the graph (@fig-mental-vs-physical) and model (@tbl-modelresults) results, depression diagnosis contributes to increase the influence of mental unwellness to physical unwellness.
+From the graph (@fig-mental-vs-physical) and model (@tbl-modelresults) results, depression diagnosis contributes to increasing the influence of mental unwellness to physical unwellness.
 Depression diagnosis, therefore, could be a moderator, which strengthens the relation between mental health (independent variable) and physical health (dependent variable).
 Other than depression diagnosis, no additional mental health issues are speculated for the purpose of this particular study.
-The result with GSS dataset, alothough not significant, support the fact that depression plays an role in impacting physical health.
+The result with the GSS dataset, although not significant, supports the fact that depression plays a role in impacting physical health.
 
 ## Gender Disparity in Health
-
 By comparing counted days of feeling mentally and physically unwell between different gender groups, we found that female respondents in general reported higher numbers of occasions feeling unwell (@fig-demo-mental and @fig-demo-physical).
-The trend could be a result of gender disparity in medical field, where women benefit less from medical research and advances because they are underrepresented as potential patients.
+The trend could be a result of gender disparity in the medical field, where women benefit less from medical research and advances because they are underrepresented as potential patients.
 The gender disparity in medical research, compounded by pervasive misogyny, translates into tangible disadvantages for female patients in real-world scenarios.
 
-From the literature review conducted by @Merone_Tsey_Russell_Nagle_2022, women continue to be significantly underrepresented in medical literature, with inadequate reporting and analysis of sex and gender in research and misogynistic perceptions persistently shape the narrative surrounding these issues.
+From the literature review conducted by @Merone_Tsey_Russell_Nagle_2022, women continue to be significantly underrepresented in medical literature, with inadequate reporting and analysis of sex and gender in research and misogynistic perceptions persistently shaping the narrative surrounding these issues.
+Medical services based on a lack of representative research make diagnoses for diseases and treatments inconvenient, inaccurate, and challenging.
+The experiences with the medical system could be one of the reasons contributing to female participants reporting higher occurrences of feeling both mentally and physically unwell.
 The result in this paper again highlights the disparity, reminding us that We still have a long way to acknowledge and solve gender and minority disparity problems in the research field.
@@
 
-There are many limitations and weakness in the analysis.
-For instance, counted days of feeling physically and mentally unwell in past 30 days might not fully capture an individual's mental and physical health status; although feeling unwell in a few days, the severity of the unwellness was not measured.
-An individual could feel seriously unwell physically or mentally, which could as well contribute to a factor for analyzing.
-On the other hand, no other mental health issues other than depression was being studied in the paper; different kinds of mental health issues could contributes to physical unwellness in different ways, further research could include those variables for a better narrative of the relationship.
+There are many limitations and weaknesses in the analysis.
+For instance, counted days of feeling physically and mentally unwell in the past 30 days might not fully capture an individual's mental and physical health status; although feeling unwell in a few days, the severity of the unwellness was not measured.
+An individual could feel seriously unwell physically or mentally, which could also contribute to a factor for analyzing.
+On the other hand, no mental health issues other than depression were studied in the paper; different kinds of mental health issues could contribute to physical unwellness in different ways, further research could include those variables for a better narrative of the relationship.
 
@@
 Lastly, by posterior predictive check, the posterior distribution indicates that the model is not doing a good job of fitting the data.
-The check result could be due to limitations of data mentioned above; furthermore, adding more relevant variables to the linear regression equation could as well improve the strength of the model.
+The check result could be due to limitations of the data mentioned above; furthermore, adding more relevant variables to the linear regression equation could as well improve the strength of the model.
 
@@
 
-In @fig-ppcheckandposteriorvsprior, we implement a posterior predictive check and compared the posterior with the prior.
-By definition, the posterior should be able to be used to simulate data similar to the actual data; however, the posterior simulated data barely recollect the characteristic of the dataset from GSS.
-This means that the model lack of strength in terms of the relationship.
+In @fig-ppcheckandposteriorvsprior, we implement a posterior predictive check and compare the posterior with the prior.
+By definition, the posterior should be able to be used to simulate data similar to the actual data; however, the posterior simulated data barely recollects the characteristics of the dataset from GSS.
+This means that the model lacks strength in terms of the relationship.
 The weakness could be a result of data limitations mentioned in [Discussion].
@@
 #| layout-ncol: 2
-#| fig-cap: "The Model Fits Barely to the Data, Hinting A Weak Model for Explaining the circumstances"
+#| fig-cap: "The Model Fits Barely to the Data, Hinting A Weak Model for Explaining the Circumstances"
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
@@
 @fig-stanareyouokay-1 is a trace plot.
-It shows lines bouncing around horizontally and have a nice overlap between the chains.
+It shows lines bouncing around horizontally and has a nice overlap between the chains.
 @fig-stanareyouokay-2 is a Rhat plot.
 From the plot, $\hat{R} = 1.05$, which is very close to 1, and ideally no more than 1.1.
-These results suggest no problems in model we built for our paper.
+These results suggest no problems in the model we built for our paper.
 

### 2024-04-23 paper/paper.qmd
Fix typo and code styling

@@
 
-Based on @tbl-modelresults, however, although having influences on linear equation in @fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = −1.43, p = .22).
+Based on @tbl-modelresults, however, although having influences on linear equation in @fig-mental-vs-physical, depression diagnosis's influences on counted days of feeling physically unwell is not significant ($\beta_2$ = 1.44, p = .22).
 Counted days of feeling mentally unwell, on the other hand, do have a significant positive correlation with counted days of feeling physically unwell ($\beta_1$ = 0.27, p = .01).
@@
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+model <-
+  readRDS(file = here::here("models/model.rds"))
 ```
@@
   list(
-    "First model" = first_model
+    "Model" = model
   ),
@@
 
-pp_check(first_model) +
+pp_check(model) +
   theme_classic() +
@@
 
-posterior_vs_prior(first_model) +
+posterior_vs_prior(model) +
   theme_minimal() +
@@
 
-plot(first_model, "trace")
+plot(model, "trace")
 
-plot(first_model, "rhat")
+plot(model, "rhat")
 ```

### 2024-04-23 scripts/00-simulate_data.R

@@ -64,7 +64,7 @@ max(simulated_data$depress) == 2
 min(simulated_data$depress) == 1
 any(unique(simulated_data$depress) == c(1:2))
 
-# expected that health is only between 1 to 4
+# expected that health is only between 1 to 4  
 max(simulated_data$health) <= 4
 min(simulated_data$health) >= 1
 any(unique(simulated_data$health) == c(1:4))

### 2024-04-23 scripts/02-data_cleaning.R

@@ -115,7 +115,7 @@ analysis_data <- mutate(analysis_data,
 )
 
 # 4. Dataset for the relationship between Numbers of days of Mental un-wellness
-# and one's health status in general
+# and one's health status in general  
 mentalVsHealth_data <- filter(GSS, ment_days >= 0) %>% filter(health >= 0)
 mentalVsHealth_data  <- select(mentalVsHealth_data, c("id", "ment_days", "health"))
 

### 2024-04-23 scripts/03-test_data.R

@@ -2,7 +2,7 @@
 # Purpose: Tests for the four dataset cleaned to make sure it is suitable for analyses
 # Author: Mingjia Chen
 # Date: 31 March 2024
-# Contact: mingjia.chen@mail.utoronto.ca
+# Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: GSS.dct, GGS.dat, data_cleaning.R
 

### 2024-04-23 scripts/04-model.R

@@ -2,7 +2,7 @@
 # Purpose: Models created and prepared for the analysis in paper.
 # Author: Mingjia Chen
 # Date: 31 March 2024
-# Contact: mingjia.chen@mail.utoronto.ca
+# Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: GSS.dct, GGS.dat, data_cleaning.R
 
@@ -17,7 +17,7 @@ path <- "data/analysis_data/analysis_data.parquet"
 analysis_data <- read_parquet(here::here(path))
 
 ### Model data ####
-first_model <-
+model <-
   stan_glm(
     formula = phys_days ~ ment_days + depress,
     data = analysis_data,
@@ -31,6 +31,6 @@ first_model <-
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  model,
+  file = "models/model.rds"
 )

### 2024-04-23 scripts/01-download_data.R
update writing

@@ -27,7 +27,8 @@
 
 # Once registered, you can access the datasets.
 # The GSS website provides a search and filter function to help you find specific datasets.
-# Select the variable names "YEAR","SEX","AGE","HEALTH","PHYSHLTH","MNTLHLTH","DEPRESS" for extracting.
+# Select the variable names "YEAR", "SEX", "AGE", "HEALTH", "PHYSHLTH", "MNTLHLTH", "DEPRESS" 
+# for extracting.
 
 
 # Step 4: Download the Data
@@ -37,5 +38,5 @@
 
 #### Save data ####
 
-# No further action is required for saving data
+# No further action is required to saving data
          
